### 2015-02-25 Doc/paper.tex
Proposal Draft

%% bare_conf.tex
%% V1.3
%% 2007/01/11
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[conference]{IEEEtran}
% Add the compsoc option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

%\usepackage{mdwmath}
%\usepackage{mdwtab}
% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
% especially mdwmath.sty and mdwtab.sty which are used to format equations
% and tables, respectively. The MDWtools set is already installed on most
% LaTeX systems. The lastest version and documentation is available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

%\usepackage{eqparbox}
% Also of notable interest is Scott Pakin's eqparbox package for creating
% (automatically sized) equal width boxes - aka "natural width parboxes".
% Available at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/

% *** SUBFIGURE PACKAGES ***
%\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures. subfigure.sty is already
% installed on most LaTeX systems. The latest version and documentation can
% be obtained at:
% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
% subfigure.sty has been superceeded by subfig.sty.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
%\usepackage[caption=false,font=footnotesize]{subfig}
%
% The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
% The latest version and documentation of caption.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Documentation is contained in the stfloats.sty comments as well as in the
% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
% does not allow \baselineskip to stretch. Authors submitting work to the
% IEEE should note that IEEE rarely uses double column equations and
% that authors should try to avoid such use. Do not be tempted to use the
% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
% not format its papers in such ways.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
% Read the url.sty source comments for usage information. Basically,
% \url{my_url_here}.

\usepackage{graphicx}
\usepackage[vlined,ruled]{algorithm2e}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{hyperref}

\usepackage{lstlisting}

\definecolor{lightgray}{rgb}{.9,.9,.9}
\definecolor{darkgray}{rgb}{.4,.4,.4}
\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mygreen}{rgb}{0,0.6,0}

\hypersetup{
    colorlinks,
    linkcolor={red},
    citecolor={blue},
    urlcolor={blue}
}

\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  commentstyle=\color{mygreen}\ttfamily,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  stringstyle=\color{purple}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}
\lstset{
  language=JavaScript,
  %backgroundcolor=\color{lightgray},
  extendedchars=true,
  basicstyle=\scriptsize\ttfamily,
  showstringspaces=false,
  showspaces=false,
  numbers=left,
  numberstyle=\tiny\color{mygray},
  numbersep=-6pt,
  tabsize=1,
  breaklines=true,
  showtabs=false,
  captionpos=b,
  numberblanklines=false,
  escapeinside=\[\]
}

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Inferring Invariants in Distributed Programs}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Keheliya Gallaba\IEEEauthorrefmark{1},
Arash Vahabzadeh\IEEEauthorrefmark{2}}
\IEEEauthorblockA{University of British Columbia\\
Vancouver, BC, Canada\\
Email: \IEEEauthorrefmark{1}kgallaba@ece.ubc.ca,
\IEEEauthorrefmark{2}arashvhb@ece.ubc.ca}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% \begin{abstract}
% %\boldmath
% The abstract goes here.
% \end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system. Building such a reliable and dependable system is not possible without thorough testing of the system. But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation. There are many failure scenarios that distributed system should handle and these scenarios should be tested as well. In some cases reproducing the failures is a difficult task e.g. degrading network performance for test purposes. Many bugs turn out to be heisenbugs in distributed system which are hard to reproduce and detect. For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as expected. One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants. This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult to the point that it is not feasible any more.

Our approach is to automatically infer these invariants. To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes. We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation. Finally we use Daikon to infer invariants among our distributed state variables.

%We are going to find invariants in distributed programs
%For that we need to find distributed state

\section{Related Work}

Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems. They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs. There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infer these distributed state variables automatically. Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these state through dynamic execution of the distributed system.

Ernst et al.\cite{ernst2001dynamically} infer invariants in a centralized program through executing the program on a collection of inputs and this invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}. Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms. To demonstrate their approach, they proved correctness of Paxos algorithm with their approach.

%2 daikon : I do not know how to describe other paper because they are basically the same
%almost-invariant
%paxos proving using dykon
\section{Approach}

The ultimate goal of this project is to infer invariants in a distributed system. For that we need to identify likely distributed state variables. We define distributed state variables,  as variables that are stored in one node whose values are affected/determined by another remote node in the distributed system. It should be noted that these variables are only a part of the state in a distributed system at a given time. For our case we assume that these capture a significant portion of the state. Consider the code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the communication between two nodes in a distributed system. The communication between the nodes can be depicted as shown in Figure~\ref{fig:sample_code_diag}. We need to infer the equality between elements in each pair \texttt{(a,first), (b,second),(sum,result)} and also the properites: \texttt{(result = a + b)} and \texttt{(sum = first + second)}.

\begin{figure}
  \includegraphics[width=\columnwidth]{sample_code.pdf}
  \caption{Example communication between two nodes in a distributed system}
  \label{fig:sample_code_diag}
\end{figure}

\begin{figure}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
    Integer a := 1
    Integer b := 2
    send ( a + '_' + b )
    recv (buf)
    Integer result := parse (buf)
\end{lstlisting}
\end{figure}

\begin{figure}
\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
    recv (buf)
    Integer first := getFirstOperand( buf )
    Integer second := getSecondOperand( buf )
    Integer sum := first + second
    send ( sum )
\end{lstlisting}
\end{figure}

\subsection{Dataflow analysis for Go programs}

In order to detect these variables, some form of dataflow analysis is required. This includes the dataflow of the distributed system as a whole and also in a single program. But currently there are no data flow analysis frameworks available for go programs.

This is a challenging problem in itself because Go language has special constructs like channels to share data between goroutines. We are planning to do this analysis dynamically by instrumenting variable declarations and assignments, and then collecting execution traces of each of these statements. We have chosen this approach because it gives information about the actual execution and therefore is more accurate. For this we are hoping to use static analysis libraries available under Go-lang tools\cite{static_golang} which provide support for Identifier resolution, Type information, Call graph navigation and Channel peers (send $\leftrightarrow$ receive) identification.

Our dynamic dataflow analysis is focused on mainly providing the following feature. Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.

As the next phase of our project, using the above analysis, we hope to find out variables affected by receiving messages in interprocess communication channels like RPC and TCP/UDP sockets. We will get the values of these variables just before another send/receive or end of function whichever occurs first. We assume these set of variables at the send statement in both (sending and receiving) nodes taken together represent global state of the distributed system.

Given two nodes which are communicating we have two such sets of variables representing a particular state. So we will select the corresponding variable pairs from send and receive of each node mentioned in the previous step and provide as inputs for the Daikon invariant detector. This will give us a set of properties that were true over the observed executions across 2 nodes. Overall execution flow of the analysis is shown in Figure~\ref{fig:go_flow}.

\begin{figure}
  \includegraphics[width=\columnwidth]{go_flow.pdf}
  \caption{Flow of the invariant inference of Go programs}
  \label{fig:go_flow}
\end{figure}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

\bibliographystyle{IEEEtran}
\bibliography{paper}
% \bibitem{IEEEhowto:kopka}
% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
%\end{thebibliography}

% that's all folks
\end{document}

### 2015-02-27 Doc/paper.tex
fixing compilation error and some typos

@@
 \usepackage{listings}
+\usepackage{listings-golang}
 \usepackage{hyperref}
-
-\usepackage{lstlisting}
 
@@
 
-\lstdefinelanguage{JavaScript}{
-  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
-  keywordstyle=\color{blue}\bfseries,
-  ndkeywords={class, export, boolean, throw, implements, import},
-  ndkeywordstyle=\color{darkgray}\bfseries,
-  identifierstyle=\color{black},
-  sensitive=false,
-  commentstyle=\color{mygreen}\ttfamily,
-  comment=[l]{//},
-  morecomment=[s]{/*}{*/},
-  stringstyle=\color{purple}\ttfamily,
-  morestring=[b]',
-  morestring=[b]"
-}
-\lstset{
-  language=JavaScript,
-  %backgroundcolor=\color{lightgray},
-  extendedchars=true,
-  basicstyle=\scriptsize\ttfamily,
+\lstset{ % add your own preferences
+    basicstyle=\footnotesize,
+    keywordstyle=\color{red},
+    numbers=left,
+    numbersep=5pt,
     showstringspaces=false, 
-  showspaces=false,
-  numbers=left,
-  numberstyle=\tiny\color{mygray},
-  numbersep=-6pt,
-  tabsize=1,
-  breaklines=true,
-  showtabs=false,
-  captionpos=b,
-  numberblanklines=false,
-  escapeinside=\[\]
+    stringstyle=\color{blue},
+    tabsize=4,
+    language=Golang % this is it !
 }
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Inferring Invariants in Distributed Programs}
+\title{Inferring Invariants of Distributed Programs}
 
@@
 They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs.
-There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infer these distributed state variables automatically.
-Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these state through dynamic execution of the distributed system.
+There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically.
+Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.
 
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a centralized program through executing the program on a collection of inputs and this invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
+Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs.
+This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
 Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables.
 Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms.
-To demonstrate their approach, they proved correctness of Paxos algorithm with their approach.
+To demonstrate their approach, they proved the correctness of the Paxos algorithm.
 
@@
 
-In order to detect these variables, some form of dataflow analysis is required.
+To detect these variables, some form of dataflow analysis is required.
 This includes the dataflow of the distributed system as a whole and also in a single program.
-But currently there are no data flow analysis frameworks available for go programs.
+But currently there are no data flow analysis frameworks available for Go programs.
 
@@
 
-Our dynamic dataflow analysis is focused on mainly providing the following feature.
+Our dynamic dataflow analysis is focused on mainly providing the following features.
 Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.

### 2015-02-27 Doc/paper.tex
Edited Introduction, Moved Related work to the end

@@
 One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants.
-This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult to the point that it is not feasible any more.
+This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult.
 
-Our approach is to automatically infer these invariants.
+Testing distributed systems is hard because a fault in a single node does not confine to that node, instead it may cause an error in another node.
+In fact errors in distributed system should be defined on global state of the system not a single node.
+In this work we assume that state of each node is comprised of its variables.
+Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state of that node.
+We refer to set of distributed state of all nodes as distributed state of the system.
+
+Our approach is to automatically infer invariants that may exist in distributed state of our system.
 To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes.
@@
 
-\section{Related Work}
-
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems.
-They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs.
-There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically.
-Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.
-
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
-Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables.
-Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms.
-To demonstrate their approach, they proved the correctness of the Paxos algorithm.
-
-%2 daikon : I do not know how to describe other paper because they are basically the same
-%almost-invariant
-%paxos proving using dykon
 \section{Approach}
@@
 
+\section{Related Work}
+
+Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems.
+They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs.
+There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically.
+Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.
+
+Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs.
+This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
+Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables.
+Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms.
+To demonstrate their approach, they proved the correctness of the Paxos algorithm.
+
+%2 daikon : I do not know how to describe other paper because they are basically the same
+%almost-invariant
+%paxos proving using dykon
+
 % trigger a \newpage just before the given reference

### 2015-03-03 Doc/paper.tex
adding line breaks to prvent future conflicts
Edited Introduction and added Background

@@
 Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system.
-Building such a reliable and dependable system is not possible without thorough testing of the system.
+Building such
+a reliable and dependable system is not possible without thorough testing of the system.
 But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
-There are many failure scenarios that distributed system should handle and these scenarios should be tested as well.
+There are many
+failure scenarios that distributed system should handle and these scenarios should be tested as well.
 In some cases reproducing the failures is a difficult task e.g.
 degrading network performance for test purposes.
-Many bugs turn out to be heisenbugs in distributed system which are hard to reproduce and detect.
-For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as expected.
-One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants.
-This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult.
+Many bugs turn out to be heisenbugs in distributed
+system which are hard to reproduce and detect.
+For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as
+expected.
+One alternative to this laborious approach is to define invariants for system's expected behaviour and check the software traces against these invariants.
+This approach is considerably easier than the former but as the system gets larger and more
+complex, providing invariants manually becomes more difficult.
 
@@
 In fact errors in distributed system should be defined on global state of the system not a single node.
-In this work we assume that state of each node is comprised of its variables.
+In this work we
+assume that state of each node is comprised of its variables.
 Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state of that node.
-We refer to set of distributed state of all nodes as distributed state of the system.
+We refer to set of distributed
+state of all nodes as distributed state of the system.
+
+\section{Background}
+
+Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is a open problem.
+To infer invariants in a distributed system we should have global snapshots (log of variables) of the system.
+However, not every snapshot of the system is a valid one.
+Mattern introduced the notion of cut and consistent cut as snapshot and valid snapshots of a system.
+In \cite{mattern1989virtual} he also proposed an algorithm to find consistent cuts.
+The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system".
+We use dynamic data flow analysis to detect distributed state of the system.
+In fact we perform data flow analysis across the nodes in the distributed system.
 
 Our approach is to automatically infer invariants that may exist in distributed state of our system.
-To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes.
+To this end, we execute distributed programs by running the test cases and dynamically select a set of variables in each node that likely represent the distributed state
+across our distributed nodes.
 We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation.
 Finally we use Daikon to infer invariants among our distributed state variables.
-
-%We are going to find invariants in distributed programs
-%For that we need to find distributed state
+We can view our approach as
+an optimization.
+The naive approach is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between variables.
+However, this naive approach is not efficient at all, if a total number of n
+instruction is executed during a run by all nodes in the system and on average we have m variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up
+finding many false positives (invariants that hold by accident and are not meaningful).
+Our approach only logs variables that a invariant might exists between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
+Another optimization that our approach does is that instead of logging the variables at each instruction, we only log them at consistent cuts annotated by developers.
+Based on our observations some must-hold invariants can be violated for small amount of time (e.g.
+execution time of several instructions) until systems goes to a stable state, so we decided to give developers responsibility to decide when invariants should hold and can be checked in the system by annotating the code.
+By this approach we improve usefulness of our tool for developers.
 
@@
 
-The ultimate goal of this project is to infer invariants in a distributed system.
-For that we need to identify likely distributed state variables.
-We define distributed state variables,  as variables that are stored in one node whose values are affected/determined by another remote node in the distributed system.
-It should be noted that these variables are only a part of the state in a distributed system at a given time.
-For our case we assume that these capture a significant portion of the state.
-Consider the code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the communication between two nodes in a distributed system.
-The communication between the nodes can be depicted as shown in Figure~\ref{fig:sample_code_diag}.
-We need to infer the equality between elements in each pair \texttt{(a,first), (b,second),(sum,result)} and also the properites: \texttt{(result = a + b)} and \texttt{(sum = first + second)}.
+The ultimate goal of this project is to infer invariants in a
+distributed system. For that we need to identify likely distributed
+state variables. We define distributed state variables,  as variables
+that are stored in one node whose values are affected/determined by
+another remote node in the distributed system. It should be noted that
+these variables are only a part of the state in a distributed system
+at a given time. For our case we assume that these capture a
+significant portion of the state. Consider the code samples
+Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
+communication between two nodes in a distributed system. The
+communication between the nodes can be depicted as shown in
+Figure~\ref{fig:sample_code_diag}. We need to infer the equality
+between elements in each pair \texttt{(a,first),
+(b,second),(sum,result)} and also the properites: \texttt{(result = a
++ b)} and \texttt{(sum = first + second)}.
 
@@
 To detect these variables, some form of dataflow analysis is required.
-This includes the dataflow of the distributed system as a whole and also in a single program.
-But currently there are no data flow analysis frameworks available for Go programs.
+This includes the dataflow of the distributed system as a whole and
+also in a single program. But currently there are no data flow
+analysis frameworks available for Go programs.
 
-This is a challenging problem in itself because Go language has special constructs like channels to share data between goroutines.
-We are planning to do this analysis dynamically by instrumenting variable declarations and assignments, and then collecting execution traces of each of these statements.
-We have chosen this approach because it gives information about the actual execution and therefore is more accurate.
-For this we are hoping to use static analysis libraries available under Go-lang tools\cite{static_golang} which provide support for Identifier resolution, Type information, Call graph navigation and Channel peers (send $\leftrightarrow$ receive) identification.
+This is a challenging problem in itself because Go language has
+special constructs like channels to share data between goroutines. We
+are planning to do this analysis dynamically by instrumenting variable
+declarations and assignments, and then collecting execution traces of
+each of these statements. We have chosen this approach because it
+gives information about the actual execution and therefore is more
+accurate. For this we are hoping to use static analysis libraries
+available under Go-lang tools\cite{static_golang} which provide
+support for Identifier resolution, Type information, Call graph
+navigation and Channel peers (send $\leftrightarrow$ receive)
+identification.
 
-Our dynamic dataflow analysis is focused on mainly providing the following features.
-Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.
+Our dynamic dataflow analysis is focused on mainly providing the
+following features. Given a variable, start line and end line it will
+return a set of variables affected by that variable between start line
+and the end line.
 
-As the next phase of our project, using the above analysis, we hope to find out variables affected by receiving messages in interprocess communication channels like RPC and TCP/UDP sockets.
-We will get the values of these variables just before another send/receive or end of function whichever occurs first.
-We assume these set of variables at the send statement in both (sending and receiving) nodes taken together represent global state of the distributed system.
+As the next phase of our project, using the above analysis, we hope to
+find out variables affected by receiving messages in interprocess
+communication channels like RPC and TCP/UDP sockets. We will get the
+values of these variables just before another send/receive or end of
+function whichever occurs first. We assume these set of variables at
+the send statement in both (sending and receiving) nodes taken
+together represent global state of the distributed system.
 
-Given two nodes which are communicating we have two such sets of variables representing a particular state.
-So we will select the corresponding variable pairs from send and receive of each node mentioned in the previous step and provide as inputs for the Daikon invariant detector.
-This will give us a set of properties that were true over the observed executions across 2 nodes.
-Overall execution flow of the analysis is shown in Figure~\ref{fig:go_flow}.
+Given two nodes which are communicating we have two such sets of
+variables representing a particular state. So we will select the
+corresponding variable pairs from send and receive of each node
+mentioned in the previous step and provide as inputs for the Daikon
+invariant detector. This will give us a set of properties that were
+true over the observed executions across 2 nodes. Overall execution
+flow of the analysis is shown in Figure~\ref{fig:go_flow}.
 
@@
 
+\section{Evaluation Methodology}
+
 \section{Related Work}
 
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems.
-They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs.
-There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically.
-Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.
+Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to
+infer almost-invariants in distributed systems. They infer the
+invariants that are true in most cases and assume these invariants
+only get violated due to manifestation of bugs. There are a number of
+ways our approach differ from theirs: Their approach requires user to
+provide a list of variables and functions that they want to consider
+for inferring invariants while our approach infers distributed state
+variables automatically. Moreover, they assume that an external module
+generates a trace of globally consistent state system for their
+algorithm while our approach extract these states through dynamic
+execution of the distributed system.
 
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
-Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables.
-Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms.
-To demonstrate their approach, they proved the correctness of the Paxos algorithm.
+Ernst et al.\cite{ernst2001dynamically} infer invariants in a
+sequential program by executing the program on a collection of inputs.
+This invariant detector has been released as a tool called
+Daikon\cite{ernst2007daikon}. Although, we use their tool to infer
+invariants, detecting invariants in a distributed system poses unique
+challenges to identify distributed state and valid global states among
+a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon
+to assist theorem provers for verifying distributed algorithms. To
+demonstrate their approach, they proved the correctness of the Paxos
+algorithm.
 

### 2015-03-03 Doc/paper.tex
v1 approach

--- 2015-02-27 Doc/paper.tex
@@
 
-Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system.
-Building such a reliable and dependable system is not possible without thorough testing of the system.
-But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
-There are many failure scenarios that distributed system should handle and these scenarios should be tested as well.
-In some cases reproducing the failures is a difficult task e.g.
-degrading network performance for test purposes.
-Many bugs turn out to be heisenbugs in distributed system which are hard to reproduce and detect.
-For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as expected.
-One alternative to this laborious approach is to define invariants for system’s expected behaviour and check the software traces against these invariants.
-This approach is considerably easier than the former but as the system gets larger and more complex, providing invariants manually becomes more difficult.
+Building a reliable distributed system is a difficult task, since
+distributed system should continue operating even when components or
+network fail, this means that there are many corner cases that
+developers should consider when building the system. Building such a
+reliable and dependable system is not possible without thorough
+testing of the system. But unfortunately testing a distributed system
+is a much more difficult task because it is much harder to test
+components of a distributed system in isolation. There are many
+failure scenarios that distributed system should handle and these
+scenarios should be tested as well. In some cases reproducing the
+failures is a difficult task e.g. degrading network performance for
+test purposes. Many bugs turn out to be heisenbugs in distributed
+system which are hard to reproduce and detect. For testing and
+debugging distributed systems, developers and testers have to spend a
+considerable amount of time inspecting logs of the system manually and
+looking for incidents that system does not behave as expected. One
+alternative to this laborious approach is to define invariants for
+system’s expected behaviour and check the software traces against
+these invariants. This approach is considerably easier than the former
+but as the system gets larger and more complex, providing invariants
+manually becomes more difficult.
 
-Testing distributed systems is hard because a fault in a single node does not confine to that node, instead it may cause an error in another node.
-In fact errors in distributed system should be defined on global state of the system not a single node.
-In this work we assume that state of each node is comprised of its variables.
-Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state of that node.
-We refer to set of distributed state of all nodes as distributed state of the system.
+Testing distributed systems is hard because a fault in a single node
+does not confine to that node, instead it may cause an error in
+another node. In fact errors in distributed system should be defined
+on global state of the system not a single node. In this work we
+assume that state of each node is comprised of its variables. Not all
+variables of one node is affected by other nodes, we define the set of
+variables of one node whose values are affected by other nodes as
+distributed state of that node. We refer to set of distributed state
+of all nodes as distributed state of the system.
 
-Our approach is to automatically infer invariants that may exist in distributed state of our system.
-To this end, we execute distributed programs and dynamically select a set of variables in each node that likely represent the distributed state across our distributed nodes.
-We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation.
-Finally we use Daikon to infer invariants among our distributed state variables.
+Our approach is to automatically infer invariants that may exist in
+distributed state of our system. To this end, we execute distributed
+programs and dynamically select a set of variables in each node that
+likely represent the distributed state across our distributed nodes.
+We do so with dynamic data flow analysis of variables and selecting
+those that are affected by a send or receive operation. Finally we use
+Daikon to infer invariants among our distributed state variables.
 
@@
 
-The ultimate goal of this project is to infer invariants in a distributed system.
-For that we need to identify likely distributed state variables.
-We define distributed state variables,  as variables that are stored in one node whose values are affected/determined by another remote node in the distributed system.
-It should be noted that these variables are only a part of the state in a distributed system at a given time.
-For our case we assume that these capture a significant portion of the state.
-Consider the code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the communication between two nodes in a distributed system.
-The communication between the nodes can be depicted as shown in Figure~\ref{fig:sample_code_diag}.
-We need to infer the equality between elements in each pair \texttt{(a,first), (b,second),(sum,result)} and also the properites: \texttt{(result = a + b)} and \texttt{(sum = first + second)}.
+The ultimate goal of this project is to infer invariants in a
+distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
+state variables. We define distributed state variables, as variables
+that are stored in one node whose values are affected or determined by
+the other remote node in the distributed system. It should be noted that
+these variables are only a part of the state in a distributed system
+at a given time. For our case we assume that these capture a
+significant portion of the state. Consider the code samples
+Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
+communication between two nodes in a distributed system. The
+communication between the nodes can be depicted as shown in
+Figure~\ref{fig:sample_code_diag}. We need to infer the equality
+between elements in each pair \texttt{(a,first),
+(b,second),(sum,result)} and also the properites: \texttt{(result = a
++ b)} and \texttt{(sum = first + second)}.
 
@@
 
+The naive approach for inferring these invariants will be to dump all
+state varaible values at all program points and feed them to an
+invariant detector like daikon\cite{ernst2007daikon}. But given the
+number of program points and huge number of variables in a relatively
+large program this approach is not scalable. So we propose 2 main
+optimizations to reduce the number of program point, variable value
+combinations.
+
+\subsection{Detecting interesting program points}
+
+Rather than dumping state at all program points we expect the
+developer to mark interesting program points using annotations. The
+program state will be dumped at only these annotated points. This will
+also help to narrow down the focus to points that are identified by
+the developer as interesting points without wasting resources
+analyzing useless program points. The annotations will be identified
+by the parser at the instrumentation phase and re-written to include
+statements which will write the values of variable to a file when the
+program reaches that point in the runtime.
+
 \subsection{Dataflow analysis for Go programs}
 
-To detect these variables, some form of dataflow analysis is required.
-This includes the dataflow of the distributed system as a whole and also in a single program.
-But currently there are no data flow analysis frameworks available for Go programs.
+Even at interesting program points, variable space that need to be
+captured is very large. So only the variables that were affected by
+the communication with other nodes need to be identified. To detect
+these variables, some form of dataflow analysis is required. This
+includes the dataflow of the distributed system as a whole and also in
+a single program. But currently there are no data flow analysis
+frameworks available for Go programs.
 
-This is a challenging problem in itself because Go language has special constructs like channels to share data between goroutines.
-We are planning to do this analysis dynamically by instrumenting variable declarations and assignments, and then collecting execution traces of each of these statements.
-We have chosen this approach because it gives information about the actual execution and therefore is more accurate.
-For this we are hoping to use static analysis libraries available under Go-lang tools\cite{static_golang} which provide support for Identifier resolution, Type information, Call graph navigation and Channel peers (send $\leftrightarrow$ receive) identification.
+This is a challenging problem in itself because Go language has
+special constructs like channels to share data between goroutines. We
+are planning to do this analysis dynamically by instrumenting variable
+declarations and assignments, and then collecting execution traces of
+each of these statements. We have chosen this approach because it
+gives information about the actual execution and therefore is more
+accurate. For this we are hoping to use static analysis libraries
+available under Go-lang tools\cite{static_golang} which provide
+support for Identifier resolution, Type information, Call graph
+navigation and Channel peers (send $\leftrightarrow$ receive)
+identification.
 
-Our dynamic dataflow analysis is focused on mainly providing the following features.
-Given a variable, start line and end line it will return a set of variables affected by that variable between start line and the end line.
+Our dynamic dataflow analysis is focused on mainly providing the
+following features. Given a variable, start line and end line it will
+return a set of variables affected by that variable between start line
+and the end line.
 
-As the next phase of our project, using the above analysis, we hope to find out variables affected by receiving messages in interprocess communication channels like RPC and TCP/UDP sockets.
-We will get the values of these variables just before another send/receive or end of function whichever occurs first.
-We assume these set of variables at the send statement in both (sending and receiving) nodes taken together represent global state of the distributed system.
+As the next phase of our project, using the above analysis, we hope to
+find out variables affected by receiving messages in interprocess
+communication channels like RPC and TCP/UDP sockets. We will get the
+values of these variables just before another send/receive or end of
+function whichever occurs first. We assume these set of variables at
+the send statement in both (sending and receiving) nodes taken
+together represent global state of the distributed system.
 
-Given two nodes which are communicating we have two such sets of variables representing a particular state.
-So we will select the corresponding variable pairs from send and receive of each node mentioned in the previous step and provide as inputs for the Daikon invariant detector.
-This will give us a set of properties that were true over the observed executions across 2 nodes.
-Overall execution flow of the analysis is shown in Figure~\ref{fig:go_flow}.
+Given two nodes which are communicating we have two such sets of
+variables representing a particular state. So we will select the
+corresponding variable pairs from send and receive of each node
+mentioned in the previous step and provide as inputs for the Daikon
+invariant detector. This will give us a set of properties that were
+true over the observed executions across 2 nodes. Overall execution
+flow of the analysis is shown in Figure~\ref{fig:go_flow}.
 
@@
 
+\subsection{Timeline}
+
 \section{Related Work}
 
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to infer almost-invariants in distributed systems.
-They infer the invariants that are true in most cases and assume these invariants only get violated due to manifestation of bugs.
-There are a number of ways our approach differ from theirs: Their approach requires user to provide a list of variables and functions that they want to consider for inferring invariants while our approach infers distributed state variables automatically.
-Moreover, they assume that an external module generates a trace of globally consistent state system for their algorithm while our approach extract these states through dynamic execution of the distributed system.
+Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to
+infer almost-invariants in distributed systems. They infer the
+invariants that are true in most cases and assume these invariants
+only get violated due to manifestation of bugs. There are a number of
+ways our approach differ from theirs: Their approach requires user to
+provide a list of variables and functions that they want to consider
+for inferring invariants while our approach infers distributed state
+variables automatically. Moreover, they assume that an external module
+generates a trace of globally consistent state system for their
+algorithm while our approach extract these states through dynamic
+execution of the distributed system.
 
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called Daikon\cite{ernst2007daikon}.
-Although, we use their tool to infer invariants, detecting invariants in a distributed system poses unique challenges to identify distributed state and valid global states among a larger set of variables.
-Ne Win et al.\cite{NeWinEGKL04} use daikon to assist theorem provers for verifying distributed algorithms.
-To demonstrate their approach, they proved the correctness of the Paxos algorithm.
+Ernst et al.\cite{ernst2001dynamically} infer invariants in a
+sequential program by executing the program on a collection of inputs.
+This invariant detector has been released as a tool called
+Daikon\cite{ernst2007daikon}. Although, we use their tool to infer
+invariants, detecting invariants in a distributed system poses unique
+challenges to identify distributed state and valid global states among
+a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon
+to assist theorem provers for verifying distributed algorithms. To
+demonstrate their approach, they proved the correctness of the Paxos
+algorithm.
 

### 2015-03-03 Doc/paper.tex

--- 2015-03-03 Doc/paper.tex
@@
 
-Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system.
-Building such
-a reliable and dependable system is not possible without thorough testing of the system.
-But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
-There are many
-failure scenarios that distributed system should handle and these scenarios should be tested as well.
-In some cases reproducing the failures is a difficult task e.g.
-degrading network performance for test purposes.
-Many bugs turn out to be heisenbugs in distributed
-system which are hard to reproduce and detect.
-For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as
-expected.
-One alternative to this laborious approach is to define invariants for system's expected behaviour and check the software traces against these invariants.
-This approach is considerably easier than the former but as the system gets larger and more
-complex, providing invariants manually becomes more difficult.
-
 Testing distributed systems is hard because a fault in a single node does not confine to that node, instead it may cause an error in another node.
@@
 The ultimate goal of this project is to infer invariants in a
-distributed system. For that we need to identify likely distributed
+distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
 state variables. We define distributed state variables, as variables
-that are stored in one node whose values are affected/determined by
-another remote node in the distributed system. It should be noted that
+that are stored in one node whose values are affected or determined by
+the other remote node in the distributed system. It should be noted that
 these variables are only a part of the state in a distributed system
@@
 
+The naive approach for inferring these invariants will be to dump all
+state varaible values at all program points and feed them to an
+invariant detector like daikon\cite{ernst2007daikon}. But given the
+number of program points and huge number of variables in a relatively
+large program this approach is not scalable. So we propose 2 main
+optimizations to reduce the number of program point, variable value
+combinations.
+
+\subsection{Detecting interesting program points}
+
+Rather than dumping state at all program points we expect the
+developer to mark interesting program points using annotations. The
+program state will be dumped at only these annotated points. This will
+also help to narrow down the focus to points that are identified by
+the developer as interesting points without wasting resources
+analyzing useless program points. The annotations will be identified
+by the parser at the instrumentation phase and re-written to include
+statements which will write the values of variable to a file when the
+program reaches that point in the runtime.
+
 \subsection{Dataflow analysis for Go programs}
 
-To detect these variables, some form of dataflow analysis is required.
-This includes the dataflow of the distributed system as a whole and
-also in a single program. But currently there are no data flow
-analysis frameworks available for Go programs.
+Even at interesting program points, variable space that need to be
+captured is very large. So only the variables that were affected by
+the communication with other nodes need to be identified. To detect
+these variables, some form of dataflow analysis is required. This
+includes the dataflow of the distributed system as a whole and also in
+a single program. But currently there are no data flow analysis
+frameworks available for Go programs.
 

### 2015-03-03 Doc/approach.tex
Breaking the paper in separate parts

--- 2015-03-03 Doc/paper.tex
@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-\usepackage{graphicx}
-\usepackage[vlined,ruled]{algorithm2e}
-\usepackage{xcolor}
-\usepackage{listings}
-\usepackage{listings-golang}
-\usepackage{hyperref}
-
-\definecolor{lightgray}{rgb}{.9,.9,.9}
-\definecolor{darkgray}{rgb}{.4,.4,.4}
-\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mygreen}{rgb}{0,0.6,0}
-
-\hypersetup{
-    colorlinks,
-    linkcolor={red},
-    citecolor={blue},
-    urlcolor={blue}
-}
-
-\lstset{ % add your own preferences
-    basicstyle=\footnotesize,
-    keywordstyle=\color{red},
-    numbers=left,
-    numbersep=5pt,
-    showstringspaces=false, 
-    stringstyle=\color{blue},
-    tabsize=4,
-    language=Golang % this is it !
-}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Inferring Invariants of Distributed Programs}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Keheliya Gallaba\IEEEauthorrefmark{1},
-Arash Vahabzadeh\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{University of British Columbia\\
-Vancouver, BC, Canada\\
-Email: \IEEEauthorrefmark{1}kgallaba@ece.ubc.ca,
-\IEEEauthorrefmark{2}arashvhb@ece.ubc.ca}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% \begin{abstract}
-% %\boldmath
-% The abstract goes here.
-% \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-
-Building a reliable distributed system is a difficult task, since
-distributed system should continue operating even when components or
-network fail, this means that there are many corner cases that
-developers should consider when building the system. Building such a
-reliable and dependable system is not possible without thorough
-testing of the system. But unfortunately testing a distributed system
-is a much more difficult task because it is much harder to test
-components of a distributed system in isolation. There are many
-failure scenarios that distributed system should handle and these
-scenarios should be tested as well. In some cases reproducing the
-failures is a difficult task e.g. degrading network performance for
-test purposes. Many bugs turn out to be heisenbugs in distributed
-system which are hard to reproduce and detect. For testing and
-debugging distributed systems, developers and testers have to spend a
-considerable amount of time inspecting logs of the system manually and
-looking for incidents that system does not behave as expected. One
-alternative to this laborious approach is to define invariants for
-system’s expected behaviour and check the software traces against
-these invariants. This approach is considerably easier than the former
-but as the system gets larger and more complex, providing invariants
-manually becomes more difficult.
-
-Testing distributed systems is hard because a fault in a single node
-does not confine to that node, instead it may cause an error in
-another node. In fact errors in distributed system should be defined
-on global state of the system not a single node. In this work we
-assume that state of each node is comprised of its variables. Not all
-variables of one node is affected by other nodes, we define the set of
-variables of one node whose values are affected by other nodes as
-distributed state of that node. We refer to set of distributed state
-of all nodes as distributed state of the system.
-
-Our approach is to automatically infer invariants that may exist in
-distributed state of our system. To this end, we execute distributed
-programs and dynamically select a set of variables in each node that
-likely represent the distributed state across our distributed nodes.
-We do so with dynamic data flow analysis of variables and selecting
-those that are affected by a send or receive operation. Finally we use
-Daikon to infer invariants among our distributed state variables.
-
-%We are going to find invariants in distributed programs
-%For that we need to find distributed state
-
 \section{Approach}
@@
 The ultimate goal of this project is to infer invariants in a
-distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
+distributed system. For that we need to identify likely distributed
 state variables. We define distributed state variables,  as variables
-that are stored in one node whose values are affected or determined by
-the other remote node in the distributed system. It should be noted that
+that are stored in one node whose values are affected/determined by
+another remote node in the distributed system. It should be noted that
 these variables are only a part of the state in a distributed system
@@
 
-The naive approach for inferring these invariants will be to dump all
-state varaible values at all program points and feed them to an
-invariant detector like daikon\cite{ernst2007daikon}. But given the
-number of program points and huge number of variables in a relatively
-large program this approach is not scalable. So we propose 2 main
-optimizations to reduce the number of program point, variable value
-combinations.
-
-\subsection{Detecting interesting program points}
-
-Rather than dumping state at all program points we expect the
-developer to mark interesting program points using annotations. The
-program state will be dumped at only these annotated points. This will
-also help to narrow down the focus to points that are identified by
-the developer as interesting points without wasting resources
-analyzing useless program points. The annotations will be identified
-by the parser at the instrumentation phase and re-written to include
-statements which will write the values of variable to a file when the
-program reaches that point in the runtime.
-
 \subsection{Dataflow analysis for Go programs}
 
-Even at interesting program points, variable space that need to be
-captured is very large. So only the variables that were affected by
-the communication with other nodes need to be identified. To detect
-these variables, some form of dataflow analysis is required. This
-includes the dataflow of the distributed system as a whole and also in
-a single program. But currently there are no data flow analysis
-frameworks available for Go programs.
+To detect these variables, some form of dataflow analysis is required.
+This includes the dataflow of the distributed system as a whole and
+also in a single program. But currently there are no data flow
+analysis frameworks available for Go programs.
 
@@
 \end{figure}
-
-\subsection{Timeline}
-
-\section{Related Work}
-
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to
-infer almost-invariants in distributed systems. They infer the
-invariants that are true in most cases and assume these invariants
-only get violated due to manifestation of bugs. There are a number of
-ways our approach differ from theirs: Their approach requires user to
-provide a list of variables and functions that they want to consider
-for inferring invariants while our approach infers distributed state
-variables automatically. Moreover, they assume that an external module
-generates a trace of globally consistent state system for their
-algorithm while our approach extract these states through dynamic
-execution of the distributed system.
-
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a
-sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called
-Daikon\cite{ernst2007daikon}. Although, we use their tool to infer
-invariants, detecting invariants in a distributed system poses unique
-challenges to identify distributed state and valid global states among
-a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon
-to assist theorem provers for verifying distributed algorithms. To
-demonstrate their approach, they proved the correctness of the Paxos
-algorithm.
-
-%2 daikon : I do not know how to describe other paper because they are basically the same
-%almost-invariant
-%paxos proving using dykon
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
-% \bibitem{IEEEhowto:kopka}
-% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%\end{thebibliography}
-
-% that's all folks
-\end{document}

### 2015-03-03 Doc/evalrelate.tex
Breaking the paper in separate parts

--- 2015-03-03 Doc/paper.tex
@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-\usepackage{graphicx}
-\usepackage[vlined,ruled]{algorithm2e}
-\usepackage{xcolor}
-\usepackage{listings}
-\usepackage{listings-golang}
-\usepackage{hyperref}
-
-\definecolor{lightgray}{rgb}{.9,.9,.9}
-\definecolor{darkgray}{rgb}{.4,.4,.4}
-\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mygreen}{rgb}{0,0.6,0}
-
-\hypersetup{
-    colorlinks,
-    linkcolor={red},
-    citecolor={blue},
-    urlcolor={blue}
-}
-
-\lstset{ % add your own preferences
-    basicstyle=\footnotesize,
-    keywordstyle=\color{red},
-    numbers=left,
-    numbersep=5pt,
-    showstringspaces=false, 
-    stringstyle=\color{blue},
-    tabsize=4,
-    language=Golang % this is it !
-}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Inferring Invariants of Distributed Programs}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Keheliya Gallaba\IEEEauthorrefmark{1},
-Arash Vahabzadeh\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{University of British Columbia\\
-Vancouver, BC, Canada\\
-Email: \IEEEauthorrefmark{1}kgallaba@ece.ubc.ca,
-\IEEEauthorrefmark{2}arashvhb@ece.ubc.ca}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% \begin{abstract}
-% %\boldmath
-% The abstract goes here.
-% \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\section{Introduction}
-
-Building a reliable distributed system is a difficult task, since
-distributed system should continue operating even when components or
-network fail, this means that there are many corner cases that
-developers should consider when building the system. Building such a
-reliable and dependable system is not possible without thorough
-testing of the system. But unfortunately testing a distributed system
-is a much more difficult task because it is much harder to test
-components of a distributed system in isolation. There are many
-failure scenarios that distributed system should handle and these
-scenarios should be tested as well. In some cases reproducing the
-failures is a difficult task e.g. degrading network performance for
-test purposes. Many bugs turn out to be heisenbugs in distributed
-system which are hard to reproduce and detect. For testing and
-debugging distributed systems, developers and testers have to spend a
-considerable amount of time inspecting logs of the system manually and
-looking for incidents that system does not behave as expected. One
-alternative to this laborious approach is to define invariants for
-system’s expected behaviour and check the software traces against
-these invariants. This approach is considerably easier than the former
-but as the system gets larger and more complex, providing invariants
-manually becomes more difficult.
-
-Testing distributed systems is hard because a fault in a single node
-does not confine to that node, instead it may cause an error in
-another node. In fact errors in distributed system should be defined
-on global state of the system not a single node. In this work we
-assume that state of each node is comprised of its variables. Not all
-variables of one node is affected by other nodes, we define the set of
-variables of one node whose values are affected by other nodes as
-distributed state of that node. We refer to set of distributed state
-of all nodes as distributed state of the system.
-
-Our approach is to automatically infer invariants that may exist in
-distributed state of our system. To this end, we execute distributed
-programs and dynamically select a set of variables in each node that
-likely represent the distributed state across our distributed nodes.
-We do so with dynamic data flow analysis of variables and selecting
-those that are affected by a send or receive operation. Finally we use
-Daikon to infer invariants among our distributed state variables.
-
-%We are going to find invariants in distributed programs
-%For that we need to find distributed state
-
-\section{Approach}
-
-The ultimate goal of this project is to infer invariants in a
-distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
-state variables. We define distributed state variables, as variables
-that are stored in one node whose values are affected or determined by
-the other remote node in the distributed system. It should be noted that
-these variables are only a part of the state in a distributed system
-at a given time. For our case we assume that these capture a
-significant portion of the state. Consider the code samples
-Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
-communication between two nodes in a distributed system. The
-communication between the nodes can be depicted as shown in
-Figure~\ref{fig:sample_code_diag}. We need to infer the equality
-between elements in each pair \texttt{(a,first),
-(b,second),(sum,result)} and also the properites: \texttt{(result = a
-+ b)} and \texttt{(sum = first + second)}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{sample_code.pdf}
-  \caption{Example communication between two nodes in a distributed system}
-  \label{fig:sample_code_diag}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
-    Integer a := 1
-    Integer b := 2
-    send ( a + '_' + b )
-    recv (buf)
-    Integer result := parse (buf)
-\end{lstlisting}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
-    recv (buf)
-    Integer first := getFirstOperand( buf )
-    Integer second := getSecondOperand( buf )
-    Integer sum := first + second
-    send ( sum )
-\end{lstlisting}
-\end{figure}
-
-The naive approach for inferring these invariants will be to dump all
-state varaible values at all program points and feed them to an
-invariant detector like daikon\cite{ernst2007daikon}. But given the
-number of program points and huge number of variables in a relatively
-large program this approach is not scalable. So we propose 2 main
-optimizations to reduce the number of program point, variable value
-combinations.
-
-\subsection{Detecting interesting program points}
-
-Rather than dumping state at all program points we expect the
-developer to mark interesting program points using annotations. The
-program state will be dumped at only these annotated points. This will
-also help to narrow down the focus to points that are identified by
-the developer as interesting points without wasting resources
-analyzing useless program points. The annotations will be identified
-by the parser at the instrumentation phase and re-written to include
-statements which will write the values of variable to a file when the
-program reaches that point in the runtime.
-
-\subsection{Dataflow analysis for Go programs}
-
-Even at interesting program points, variable space that need to be
-captured is very large. So only the variables that were affected by
-the communication with other nodes need to be identified. To detect
-these variables, some form of dataflow analysis is required. This
-includes the dataflow of the distributed system as a whole and also in
-a single program. But currently there are no data flow analysis
-frameworks available for Go programs.
-
-This is a challenging problem in itself because Go language has
-special constructs like channels to share data between goroutines. We
-are planning to do this analysis dynamically by instrumenting variable
-declarations and assignments, and then collecting execution traces of
-each of these statements. We have chosen this approach because it
-gives information about the actual execution and therefore is more
-accurate. For this we are hoping to use static analysis libraries
-available under Go-lang tools\cite{static_golang} which provide
-support for Identifier resolution, Type information, Call graph
-navigation and Channel peers (send $\leftrightarrow$ receive)
-identification.
-
-Our dynamic dataflow analysis is focused on mainly providing the
-following features. Given a variable, start line and end line it will
-return a set of variables affected by that variable between start line
-and the end line.
-
-As the next phase of our project, using the above analysis, we hope to
-find out variables affected by receiving messages in interprocess
-communication channels like RPC and TCP/UDP sockets. We will get the
-values of these variables just before another send/receive or end of
-function whichever occurs first. We assume these set of variables at
-the send statement in both (sending and receiving) nodes taken
-together represent global state of the distributed system.
-
-Given two nodes which are communicating we have two such sets of
-variables representing a particular state. So we will select the
-corresponding variable pairs from send and receive of each node
-mentioned in the previous step and provide as inputs for the Daikon
-invariant detector. This will give us a set of properties that were
-true over the observed executions across 2 nodes. Overall execution
-flow of the analysis is shown in Figure~\ref{fig:go_flow}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{go_flow.pdf}
-  \caption{Flow of the invariant inference of Go programs}
-  \label{fig:go_flow}
-\end{figure}
-
-\subsection{Timeline}
+\section{Evaluation Methodology}
 
@@
 algorithm.
-
-%2 daikon : I do not know how to describe other paper because they are basically the same
-%almost-invariant
-%paxos proving using dykon
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
-% \bibitem{IEEEhowto:kopka}
-% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%\end{thebibliography}
-
-% that's all folks
-\end{document}

### 2015-03-03 Doc/introback.tex
Breaking the paper in separate parts

--- 2015-03-03 Doc/paper.tex
@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-\ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  % \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-%\usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-\usepackage{graphicx}
-\usepackage[vlined,ruled]{algorithm2e}
-\usepackage{xcolor}
-\usepackage{listings}
-\usepackage{listings-golang}
-\usepackage{hyperref}
-
-\definecolor{lightgray}{rgb}{.9,.9,.9}
-\definecolor{darkgray}{rgb}{.4,.4,.4}
-\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
-\definecolor{mygray}{rgb}{0.5,0.5,0.5}
-\definecolor{mygreen}{rgb}{0,0.6,0}
-
-\hypersetup{
-    colorlinks,
-    linkcolor={red},
-    citecolor={blue},
-    urlcolor={blue}
-}
-
-\lstset{ % add your own preferences
-    basicstyle=\footnotesize,
-    keywordstyle=\color{red},
-    numbers=left,
-    numbersep=5pt,
-    showstringspaces=false, 
-    stringstyle=\color{blue},
-    tabsize=4,
-    language=Golang % this is it !
-}
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
-
-\begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-\title{Inferring Invariants of Distributed Programs}
-
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-\author{\IEEEauthorblockN{Keheliya Gallaba\IEEEauthorrefmark{1},
-Arash Vahabzadeh\IEEEauthorrefmark{2}}
-\IEEEauthorblockA{University of British Columbia\\
-Vancouver, BC, Canada\\
-Email: \IEEEauthorrefmark{1}kgallaba@ece.ubc.ca,
-\IEEEauthorrefmark{2}arashvhb@ece.ubc.ca}}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
-\maketitle
-
-% \begin{abstract}
-% %\boldmath
-% The abstract goes here.
-% \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
 \section{Introduction}
@@
 state of all nodes as distributed state of the system.
+
+The most challenging part of this work is to find valid snapshots of distributed states for the system.
 
@@
 By this approach we improve usefulness of our tool for developers.
-
-\section{Approach}
-
-The ultimate goal of this project is to infer invariants in a
-distributed system. For that we need to identify likely distributed
-state variables. We define distributed state variables,  as variables
-that are stored in one node whose values are affected/determined by
-another remote node in the distributed system. It should be noted that
-these variables are only a part of the state in a distributed system
-at a given time. For our case we assume that these capture a
-significant portion of the state. Consider the code samples
-Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
-communication between two nodes in a distributed system. The
-communication between the nodes can be depicted as shown in
-Figure~\ref{fig:sample_code_diag}. We need to infer the equality
-between elements in each pair \texttt{(a,first),
-(b,second),(sum,result)} and also the properites: \texttt{(result = a
-+ b)} and \texttt{(sum = first + second)}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{sample_code.pdf}
-  \caption{Example communication between two nodes in a distributed system}
-  \label{fig:sample_code_diag}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
-    Integer a := 1
-    Integer b := 2
-    send ( a + '_' + b )
-    recv (buf)
-    Integer result := parse (buf)
-\end{lstlisting}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
-    recv (buf)
-    Integer first := getFirstOperand( buf )
-    Integer second := getSecondOperand( buf )
-    Integer sum := first + second
-    send ( sum )
-\end{lstlisting}
-\end{figure}
-
-\subsection{Dataflow analysis for Go programs}
-
-To detect these variables, some form of dataflow analysis is required.
-This includes the dataflow of the distributed system as a whole and
-also in a single program. But currently there are no data flow
-analysis frameworks available for Go programs.
-
-This is a challenging problem in itself because Go language has
-special constructs like channels to share data between goroutines. We
-are planning to do this analysis dynamically by instrumenting variable
-declarations and assignments, and then collecting execution traces of
-each of these statements. We have chosen this approach because it
-gives information about the actual execution and therefore is more
-accurate. For this we are hoping to use static analysis libraries
-available under Go-lang tools\cite{static_golang} which provide
-support for Identifier resolution, Type information, Call graph
-navigation and Channel peers (send $\leftrightarrow$ receive)
-identification.
-
-Our dynamic dataflow analysis is focused on mainly providing the
-following features. Given a variable, start line and end line it will
-return a set of variables affected by that variable between start line
-and the end line.
-
-As the next phase of our project, using the above analysis, we hope to
-find out variables affected by receiving messages in interprocess
-communication channels like RPC and TCP/UDP sockets. We will get the
-values of these variables just before another send/receive or end of
-function whichever occurs first. We assume these set of variables at
-the send statement in both (sending and receiving) nodes taken
-together represent global state of the distributed system.
-
-Given two nodes which are communicating we have two such sets of
-variables representing a particular state. So we will select the
-corresponding variable pairs from send and receive of each node
-mentioned in the previous step and provide as inputs for the Daikon
-invariant detector. This will give us a set of properties that were
-true over the observed executions across 2 nodes. Overall execution
-flow of the analysis is shown in Figure~\ref{fig:go_flow}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{go_flow.pdf}
-  \caption{Flow of the invariant inference of Go programs}
-  \label{fig:go_flow}
-\end{figure}
-
-\section{Evaluation Methodology}
-
-\section{Related Work}
-
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to
-infer almost-invariants in distributed systems. They infer the
-invariants that are true in most cases and assume these invariants
-only get violated due to manifestation of bugs. There are a number of
-ways our approach differ from theirs: Their approach requires user to
-provide a list of variables and functions that they want to consider
-for inferring invariants while our approach infers distributed state
-variables automatically. Moreover, they assume that an external module
-generates a trace of globally consistent state system for their
-algorithm while our approach extract these states through dynamic
-execution of the distributed system.
-
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a
-sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called
-Daikon\cite{ernst2007daikon}. Although, we use their tool to infer
-invariants, detecting invariants in a distributed system poses unique
-challenges to identify distributed state and valid global states among
-a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon
-to assist theorem provers for verifying distributed algorithms. To
-demonstrate their approach, they proved the correctness of the Paxos
-algorithm.
-
-%2 daikon : I do not know how to describe other paper because they are basically the same
-%almost-invariant
-%paxos proving using dykon
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
-
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
-% \bibitem{IEEEhowto:kopka}
-% H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%   0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-%\end{thebibliography}
-
-% that's all folks
-\end{document}

### 2015-03-03 Doc/paper.tex
Breaking the paper in separate parts

--- 2015-03-03 Doc/paper.tex
@@
 
-\section{Introduction}
+\input{introback}
 
-Building a reliable distributed system is a difficult task, since
-distributed system should continue operating even when components or
-network fail, this means that there are many corner cases that
-developers should consider when building the system. Building such a
-reliable and dependable system is not possible without thorough
-testing of the system. But unfortunately testing a distributed system
-is a much more difficult task because it is much harder to test
-components of a distributed system in isolation. There are many
-failure scenarios that distributed system should handle and these
-scenarios should be tested as well. In some cases reproducing the
-failures is a difficult task e.g. degrading network performance for
-test purposes. Many bugs turn out to be heisenbugs in distributed
-system which are hard to reproduce and detect. For testing and
-debugging distributed systems, developers and testers have to spend a
-considerable amount of time inspecting logs of the system manually and
-looking for incidents that system does not behave as expected. One
-alternative to this laborious approach is to define invariants for
-system’s expected behaviour and check the software traces against
-these invariants. This approach is considerably easier than the former
-but as the system gets larger and more complex, providing invariants
-manually becomes more difficult.
+\input{approach}
 
-Testing distributed systems is hard because a fault in a single node
-does not confine to that node, instead it may cause an error in
-another node. In fact errors in distributed system should be defined
-on global state of the system not a single node. In this work we
-assume that state of each node is comprised of its variables. Not all
-variables of one node is affected by other nodes, we define the set of
-variables of one node whose values are affected by other nodes as
-distributed state of that node. We refer to set of distributed state
-of all nodes as distributed state of the system.
-
-Our approach is to automatically infer invariants that may exist in
-distributed state of our system. To this end, we execute distributed
-programs and dynamically select a set of variables in each node that
-likely represent the distributed state across our distributed nodes.
-We do so with dynamic data flow analysis of variables and selecting
-those that are affected by a send or receive operation. Finally we use
-Daikon to infer invariants among our distributed state variables.
-
-%We are going to find invariants in distributed programs
-%For that we need to find distributed state
-
-\section{Approach}
-
-The ultimate goal of this project is to infer invariants in a
-distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
-state variables. We define distributed state variables, as variables
-that are stored in one node whose values are affected or determined by
-the other remote node in the distributed system. It should be noted that
-these variables are only a part of the state in a distributed system
-at a given time. For our case we assume that these capture a
-significant portion of the state. Consider the code samples
-Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
-communication between two nodes in a distributed system. The
-communication between the nodes can be depicted as shown in
-Figure~\ref{fig:sample_code_diag}. We need to infer the equality
-between elements in each pair \texttt{(a,first),
-(b,second),(sum,result)} and also the properites: \texttt{(result = a
-+ b)} and \texttt{(sum = first + second)}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{sample_code.pdf}
-  \caption{Example communication between two nodes in a distributed system}
-  \label{fig:sample_code_diag}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
-    Integer a := 1
-    Integer b := 2
-    send ( a + '_' + b )
-    recv (buf)
-    Integer result := parse (buf)
-\end{lstlisting}
-\end{figure}
-
-\begin{figure}
-\begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
-    recv (buf)
-    Integer first := getFirstOperand( buf )
-    Integer second := getSecondOperand( buf )
-    Integer sum := first + second
-    send ( sum )
-\end{lstlisting}
-\end{figure}
-
-The naive approach for inferring these invariants will be to dump all
-state varaible values at all program points and feed them to an
-invariant detector like daikon\cite{ernst2007daikon}. But given the
-number of program points and huge number of variables in a relatively
-large program this approach is not scalable. So we propose 2 main
-optimizations to reduce the number of program point, variable value
-combinations.
-
-\subsection{Detecting interesting program points}
-
-Rather than dumping state at all program points we expect the
-developer to mark interesting program points using annotations. The
-program state will be dumped at only these annotated points. This will
-also help to narrow down the focus to points that are identified by
-the developer as interesting points without wasting resources
-analyzing useless program points. The annotations will be identified
-by the parser at the instrumentation phase and re-written to include
-statements which will write the values of variable to a file when the
-program reaches that point in the runtime.
-
-\subsection{Dataflow analysis for Go programs}
-
-Even at interesting program points, variable space that need to be
-captured is very large. So only the variables that were affected by
-the communication with other nodes need to be identified. To detect
-these variables, some form of dataflow analysis is required. This
-includes the dataflow of the distributed system as a whole and also in
-a single program. But currently there are no data flow analysis
-frameworks available for Go programs.
-
-This is a challenging problem in itself because Go language has
-special constructs like channels to share data between goroutines. We
-are planning to do this analysis dynamically by instrumenting variable
-declarations and assignments, and then collecting execution traces of
-each of these statements. We have chosen this approach because it
-gives information about the actual execution and therefore is more
-accurate. For this we are hoping to use static analysis libraries
-available under Go-lang tools\cite{static_golang} which provide
-support for Identifier resolution, Type information, Call graph
-navigation and Channel peers (send $\leftrightarrow$ receive)
-identification.
-
-Our dynamic dataflow analysis is focused on mainly providing the
-following features. Given a variable, start line and end line it will
-return a set of variables affected by that variable between start line
-and the end line.
-
-As the next phase of our project, using the above analysis, we hope to
-find out variables affected by receiving messages in interprocess
-communication channels like RPC and TCP/UDP sockets. We will get the
-values of these variables just before another send/receive or end of
-function whichever occurs first. We assume these set of variables at
-the send statement in both (sending and receiving) nodes taken
-together represent global state of the distributed system.
-
-Given two nodes which are communicating we have two such sets of
-variables representing a particular state. So we will select the
-corresponding variable pairs from send and receive of each node
-mentioned in the previous step and provide as inputs for the Daikon
-invariant detector. This will give us a set of properties that were
-true over the observed executions across 2 nodes. Overall execution
-flow of the analysis is shown in Figure~\ref{fig:go_flow}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{go_flow.pdf}
-  \caption{Flow of the invariant inference of Go programs}
-  \label{fig:go_flow}
-\end{figure}
-
-\subsection{Timeline}
-
-\section{Related Work}
-
-Yabandeh et al.\cite{yabandeh2011finding} proposed an approach to
-infer almost-invariants in distributed systems. They infer the
-invariants that are true in most cases and assume these invariants
-only get violated due to manifestation of bugs. There are a number of
-ways our approach differ from theirs: Their approach requires user to
-provide a list of variables and functions that they want to consider
-for inferring invariants while our approach infers distributed state
-variables automatically. Moreover, they assume that an external module
-generates a trace of globally consistent state system for their
-algorithm while our approach extract these states through dynamic
-execution of the distributed system.
-
-Ernst et al.\cite{ernst2001dynamically} infer invariants in a
-sequential program by executing the program on a collection of inputs.
-This invariant detector has been released as a tool called
-Daikon\cite{ernst2007daikon}. Although, we use their tool to infer
-invariants, detecting invariants in a distributed system poses unique
-challenges to identify distributed state and valid global states among
-a larger set of variables. Ne Win et al.\cite{NeWinEGKL04} use daikon
-to assist theorem provers for verifying distributed algorithms. To
-demonstrate their approach, they proved the correctness of the Paxos
-algorithm.
+\input{evalrelate}
 

### 2015-03-04 Doc/approach.tex
approach iter 2

@@
 The ultimate goal of this project is to infer invariants in a
-distributed system. For the scope of this project we will consider a system with 2 nodes. Before inferring invariants we need to identify likely distributed
-state variables. We define distributed state variables, as variables
-that are stored in one node whose values are affected or determined by
-the other remote node in the distributed system. It should be noted that
-these variables are only a part of the state in a distributed system
-at a given time. For our case we assume that these capture a
-significant portion of the state. Consider the code samples
-Listing~\ref{lst:node0} and Listing~\ref{lst:node1} showing the
-communication between two nodes in a distributed system. The
-communication between the nodes can be depicted as shown in
-Figure~\ref{fig:sample_code_diag}. We need to infer the equality
-between elements in each pair \texttt{(a,first),
+distributed system. For the scope of this project we will consider a
+system with 2 nodes. Before inferring invariants we need to identify
+likely distributed state variables. We define distributed state
+variables, as variables that are stored in one node whose values are
+affected or determined by the other remote node in the distributed
+system. It should be noted that these variables are only a part of the
+state in a distributed system at a given time. For our case we assume
+that these capture a significant portion of the state. Consider the
+code samples Listing~\ref{lst:node0} and Listing~\ref{lst:node1}
+showing the communication between two nodes in a distributed system.
+This conversation is depicted visually in
+Figure~\ref{fig:sample_code_diag}. Here it will be useful to to infer
+the equality between elements in each pair \texttt{(a,first),
 (b,second),(sum,result)} and also the properites: \texttt{(result = a
@@
 number of program points and huge number of variables in a relatively
-large program this approach is not scalable. So we propose 2 main
+large program this approach is not scalable. So we propose two main
 optimizations to reduce the number of program point, variable value
@@
 program reaches that point in the runtime.
+
+Since there can be multiple points annotated in a program by a
+developer, vector clocks will be used to partially order annotation
+pairs in the two programs. This will also help to invalidate
+annotations put at irrelevant locations by the developer.
 

### 2015-03-04 Doc/evalrelate.tex
Added Motivation Example

@@
 algorithm.
+
+Beschastnikh et al \cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system.
+By using logs of the system, they put the responsibility on developers to decide which portion of state of the program can be used to infer invariants.
+We require developers at which point in program invariants can be checked but we infer the portion of state that can be checked for invariants automatically with data flow analysis.
+
+\section{Acknowledgment}
+We thank Ivan Beschastnikh for his valuable feedback on initial drafts of this proposal.

### 2015-03-04 Doc/introback.tex
Added Motivation Example

@@
 a reliable and dependable system is not possible without thorough testing of the system.
-But unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
+However, unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
 There are many
@@
 
-The most challenging part of this work is to find valid snapshots of distributed states for the system.
+%The most challenging part of this work is to find valid snapshots of distributed states for the system.
+
+\section{Motivating Example}
+For motivation example, consider sudo-2-phase-commit protocol of figure \ref{lst:2pc}.
+In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``True" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
+The correctness invariant of this protocol is that at the end of protocol value of commit variable of all nodes should be the same.
+
+\begin{figure}
+\begin{lstlisting}[caption={Coordinator Code}]
+for i := 1 to n do
+	send('Q',i)
+commit := decide()
+for i:= 1 to n do
+	recv(buf,i)
+	if (buf == 'A')
+		commit := 'A'
+for i := 1 to n
+	send(commit, i)
+\end{lstlisting}
+\begin{lstlisting}[caption={Coordinator Code}]
+recv(buf)
+if(buf == 'Q')
+	vote:= decide()
+	send(vote)
+if (vote == 'A')
+	commit = 'A'
+else
+	recv(buf)
+	commit = buf
+\end{lstlisting}
+\caption{Sudo 2 phase commit code for coordinator and cohorts}
+\label{lst:2pc}
+\end{figure}
 
@@
 
+Invariants are properties that should hold in  certain points in program.
 Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is a open problem.
@@
 Finally we use Daikon to infer invariants among our distributed state variables.
-We can view our approach as
-an optimization.
-The naive approach is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between variables.
-However, this naive approach is not efficient at all, if a total number of n
-instruction is executed during a run by all nodes in the system and on average we have m variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up
-finding many false positives (invariants that hold by accident and are not meaningful).
-Our approach only logs variables that a invariant might exists between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
+\\ \\
+We can view our approach as an optimization.
+The naive approach is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between the variables.
+However, this naive approach is not efficient at all, if a total number of n instruction is executed during a run by all nodes in the system and on average we have m variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up finding many false positives (invariants that hold by accident and are not meaningful).
+Our approach only logs variables that an invariant might exists between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
 Another optimization that our approach does is that instead of logging the variables at each instruction, we only log them at consistent cuts annotated by developers.
@@
 By this approach we improve usefulness of our tool for developers.
+Another approach can be inferring the invariants from logs of the system, our approach removes the burden from developers to decide which portion of node's state needs to be logged.
+We automatically infer variables that are likely to have invariants between them with data flow analysis.

### 2015-03-04 Doc/approach.tex
temp back up

@@
 pairs in the two programs. This will also help to invalidate
-annotations put at irrelevant locations by the developer.
+annotations inserted at irrelevant locations by the developer.
 
@@
 includes the dataflow of the distributed system as a whole and also in
-a single program. But currently there are no data flow analysis
-frameworks available for Go programs.
+a single program.
+For example using a forward flow analysis on Listing~\ref{lst:node1} we can say that \texttt{sum} variable at line 4 and line 5 is affected by the \texttt{buf} variable at line 1.
+But currently there are no data flow analysis
+frameworks specifically for Go programs.
 
-This is a challenging problem in itself because Go language has
-special constructs like channels to share data between goroutines. We
-are planning to do this analysis dynamically by instrumenting variable
-declarations and assignments, and then collecting execution traces of
-each of these statements. We have chosen this approach because it
-gives information about the actual execution and therefore is more
-accurate. For this we are hoping to use static analysis libraries
-available under Go-lang tools\cite{static_golang} which provide
-support for Identifier resolution, Type information, Call graph
-navigation and Channel peers (send $\leftrightarrow$ receive)
-identification.
+% This is a challenging problem in itself because Go language has
+% special constructs like channels to share data between goroutines. We
+% are planning to do this analysis dynamically by instrumenting variable
+% declarations and assignments, and then collecting execution traces of
+% each of these statements. We have chosen this approach because it
+% gives information about the actual execution and therefore is more
+% accurate. For this we are hoping to use static analysis libraries
+% available under Go-lang tools\cite{static_golang} which provide
+% support for Identifier resolution, Type information, Call graph
+% navigation and Channel peers (send $\leftrightarrow$ receive)
+% identification.
 
-Our dynamic dataflow analysis is focused on mainly providing the
-following features. Given a variable, start line and end line it will
-return a set of variables affected by that variable between start line
-and the end line.
+% Our dynamic dataflow analysis is focused on mainly providing the
+% following features. Given a variable, start line and end line it will
+% return a set of variables affected by that variable between start line
+% and the end line.
 
-As the next phase of our project, using the above analysis, we hope to
-find out variables affected by receiving messages in interprocess
-communication channels like RPC and TCP/UDP sockets. We will get the
-values of these variables just before another send/receive or end of
-function whichever occurs first. We assume these set of variables at
-the send statement in both (sending and receiving) nodes taken
-together represent global state of the distributed system.
+% As the next phase of our project, using the above analysis, we hope to
+% find out variables affected by receiving messages in interprocess
+% communication channels like RPC and TCP/UDP sockets. We will get the
+% values of these variables just before another send/receive or end of
+% function whichever occurs first. We assume these set of variables at
+% the send statement in both (sending and receiving) nodes taken
+% together represent global state of the distributed system.
 
-Given two nodes which are communicating we have two such sets of
-variables representing a particular state. So we will select the
-corresponding variable pairs from send and receive of each node
-mentioned in the previous step and provide as inputs for the Daikon
-invariant detector. This will give us a set of properties that were
-true over the observed executions across 2 nodes. Overall execution
-flow of the analysis is shown in Figure~\ref{fig:go_flow}.
+% Given two nodes which are communicating we have two such sets of
+% variables representing a particular state. So we will select the
+% corresponding variable pairs from send and receive of each node
+% mentioned in the previous step and provide as inputs for the Daikon
+% invariant detector. This will give us a set of properties that were
+% true over the observed executions across 2 nodes. Overall execution
+% flow of the analysis is shown in Figure~\ref{fig:go_flow}.
 

### 2015-03-04 Doc/approach.tex
dataflow details

@@
 
+So we are planning to do a dynamic dataflow analysis which consists of follwing steps:
+\begin{itemize}
+\item Instrumenting variable declarations and assignments at the run time
+\item Collecting execution traces of each of these statements by runnning test suites
+\item Doing a forward flow analysis using the collected traces
+\end{itemize}
+
+This dynamic analysis approach was chosen because it gives information about the actual execution and therefore is more accurate.
+And also compared to using a static analysis-based approach, this approach makes it easier to handle Go language-specific constructs like channels which are used share data between goroutines.
+Only drawback in this approach is, it only examines the paths invoked during execution, unlike static analysis which can be used to reason about all possible execution paths and variable values.
+To compensate for that we are planning to use a comprehnsive test suite with good test coverage.
+
 % This is a challenging problem in itself because Go language has

### 2015-03-04 Doc/introback.tex
Editing Introduction

@@
 For motivation example, consider sudo-2-phase-commit protocol of figure \ref{lst:2pc}.
-In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``True" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
-The correctness invariant of this protocol is that at the end of protocol value of commit variable of all nodes should be the same.
+In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
+At the end of this protocol all nodes should either commit or abort .
+In order to verify that this algorithm is working correctly, developer can examine inferred invariants of the protocol run and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value).
+We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between variables.
 
 \begin{figure}
+\centering
 \begin{lstlisting}[caption={Coordinator Code}]

### 2015-03-04 Doc/evalrelate.tex
Editing Introduction
Added Evaluation

@@
 \section{Evaluation Methodology}
+We will implement our approach in a tool in Go programming language.
+We plan to evaluate our tool by verifying correctness of two phase commit and leader election protocols.
+Our tool should be able to infer safety property of both algorithms.
+In two phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property.
+In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property).
+It is worth mentioning that our approach is not suitable for checking the liveness properties of these algorithms.
 

### 2015-03-04 Doc/approach.tex
execution flow added

@@
 
-So we are planning to do a dynamic dataflow analysis which consists of follwing steps:
+So we are planning to do a dynamic dataflow analysis which consists of following steps:
 \begin{itemize}
@@
 
+Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
+\begin{itemize}
+\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
+\item Program is instrumented to 
+\begin{itemize}
+\item dump variable values at the annotated program points at run time
+\item wrap all RPC communication to include vector clocks
+\item log all declarations and assignments for doing the forward flow analysis
+\end{itemize}
+ For this we are hoping to use static analysis libraries
+available under Go-lang Parse package and tools\cite{static_golang} which provide
+support for Identifier resolution, Type information, Call graph
+navigation and Channel peers (send $\leftrightarrow$ receive)
+identification.
+\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
+\item Forward flow analysis is done on the collected traces
+\item Using the results of the previous step, variables contributing to distributed state is identified.
+\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
+\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
+\end{itemize}
+
 \begin{figure}
@@
 \end{figure}
+
+\section{Timeline}

### 2015-03-04 Doc/evalrelate.tex
Edited Intro

@@
 
-Beschastnikh et al \cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system.
+Beschastnikh et al.
+\cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system.
 By using logs of the system, they put the responsibility on developers to decide which portion of state of the program can be used to infer invariants.
-We require developers at which point in program invariants can be checked but we infer the portion of state that can be checked for invariants automatically with data flow analysis.
+We require developers to specify at which points in program invariants can be checked but we infer the portion of the state that can be checked for invariants automatically with data flow analysis.
 

### 2015-03-04 Doc/introback.tex
Edited Intro

@@
 a reliable and dependable system is not possible without thorough testing of the system.
-However, unfortunately testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
+However, testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
 There are many
@@
 
-Testing distributed systems is hard because a fault in a single node does not confine to that node, instead it may cause an error in another node.
-In fact errors in distributed system should be defined on global state of the system not a single node.
+Testing distributed systems is hard because a fault in a single node does not confine to that node, instead, it may cause an error in another node.
+In fact errors in distributed system should be defined on global state of the system and not on a single node.
 In this work we
 assume that state of each node is comprised of its variables.
-Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state of that node.
+Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node.
 We refer to set of distributed
-state of all nodes as distributed state of the system.
+state variables of all nodes as distributed state of the system.
 
@@
 \section{Motivating Example}
-For motivation example, consider sudo-2-phase-commit protocol of figure \ref{lst:2pc}.
+For motivation example, consider sudo-two-phase-commit protocol of figure \ref{lst:2pc}.
 In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
 At the end of this protocol all nodes should either commit or abort .
-In order to verify that this algorithm is working correctly, developer can examine inferred invariants of the protocol run and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value).
-We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between variables.
+In order to verify that this algorithm is working correctly, developers can examine inferred invariants of the protocol execution and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value and this property should be inferred by executing the protocol).
+We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
 
@@
 \end{lstlisting}
-\caption{Sudo 2 phase commit code for coordinator and cohorts}
+\caption{Sudo two phase commit code for coordinator and cohorts}
 \label{lst:2pc}
@@
 In \cite{mattern1989virtual} he also proposed an algorithm to find consistent cuts.
-The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system".
-We use dynamic data flow analysis to detect distributed state of the system.
-In fact we perform data flow analysis across the nodes in the distributed system.
+The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes consists a significant portion of distributed state of that node.
+We use dynamic data flow analysis to detect the distributed state of the system.
+We also use vector clocks to partially order snapshots of the nodes in our system and form consistent cuts.
 
@@
 We can view our approach as an optimization.
-The naive approach is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between the variables.
+The naive approach to solve inference problem is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between the variables.
 However, this naive approach is not efficient at all, if a total number of n instruction is executed during a run by all nodes in the system and on average we have m variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up finding many false positives (invariants that hold by accident and are not meaningful).
-Our approach only logs variables that an invariant might exists between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
+Our approach only logs variables that an invariant might exist between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
 Another optimization that our approach does is that instead of logging the variables at each instruction, we only log them at consistent cuts annotated by developers.
-Based on our observations some must-hold invariants can be violated for small amount of time (e.g.
-execution time of several instructions) until systems goes to a stable state, so we decided to give developers responsibility to decide when invariants should hold and can be checked in the system by annotating the code.
+Based on our observation some must-hold invariants can be violated for small amount of time (e.g.
+execution time of several instructions) until systems goes to a stable state, so we decided to give developers responsibility to decide at which points in program invariants should hold and can be checked by annotating the code.
 By this approach we improve usefulness of our tool for developers.
-Another approach can be inferring the invariants from logs of the system, our approach removes the burden from developers to decide which portion of node's state needs to be logged.
+Another approach can be inferring the invariants from logs of the system, our approach removes the burden from developers to decide which portion of each node's state needs to be logged.
 We automatically infer variables that are likely to have invariants between them with data flow analysis.

### 2015-03-04 Doc/approach.tex
timeline

@@
 \section{Timeline}
+
+Following is the planned milestones and estimated timeline for the project completion.
+
+\begin{description}
+  \item[2/10:] Proposal Draft Submission
+  \item[3/3:] Proposal Submission
+  \item[3/7:] Finalizing the design, Familirization with required tools (Daikon, Go source analysis tools)
+  \item[3/14:] Implementation - Go program instrumentation to handle annotations and dumping state
+  \item[3/21:] Implementation - Dynamic Forward Analysis for Go programs
+  \item[3/28:] Implementation - Vector clocks integration and end-to-end working analysis
+  \item[4/4:] Evaluation - Inferring invariants in test programs
+  \item[4/7:] Project Presentation
+  \item[4/16:] Project Code and Report Submission
+\end{description}

### 2015-03-04 Doc/evalrelate.tex
Edited Related Work

@@
 We will implement our approach in a tool in Go programming language.
-We plan to evaluate our tool by verifying correctness of two phase commit and leader election protocols.
+We plan to evaluate our tool by verifying correctness of two-phase commit and leader election protocols.
 Our tool should be able to infer safety property of both algorithms.
-In two phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property.
+In two-phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property.
 In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property).
@@
 \cite{temporalInv} infer temporal invariants from partially ordered logs of the distributed system.
-By using logs of the system, they put the responsibility on developers to decide which portion of state of the program can be used to infer invariants.
-We require developers to specify at which points in program invariants can be checked but we infer the portion of the state that can be checked for invariants automatically with data flow analysis.
+By using logs of the system, they put the responsibility on developers to decide which portion of the state of the program can be used to infer invariants.
+Although, we require developers to specify at which points in the program invariants can be checked, we infer the portion of the state that can be checked for invariants automatically with data flow analysis.
 
 \section{Acknowledgment}
-We thank Ivan Beschastnikh for his valuable feedback on initial drafts of this proposal.
+We would like to thank Ivan Beschastnikh for his valuable insight and feedback on initial draft of this proposal.

### 2015-04-03 Doc/introback.tex
some typos

@@
 \section{Motivating Example}
-For motivation example, consider sudo-two-phase-commit protocol of figure \ref{lst:2pc}.
+For motivation example, consider pseudo-two-phase-commit protocol of figure \ref{lst:2pc}.
 In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
@@
 \end{lstlisting}
-\caption{Sudo two phase commit code for coordinator and cohorts}
+\caption{Pseudo two phase commit code for coordinator and cohorts}
 \label{lst:2pc}

### 2015-04-03 src/instrumenter.go
init src

@@ -1,0 +1,79 @@
+package main
+
+import (
+	//"bytes"
+	"fmt"
+	"go/ast"
+	//"go/format"
+	"go/parser"
+	//"go/printer"
+	"go/token"
+	//"os"
+	"strings"
+)
+
+func main() {
+	src := `
+// This is the package comment.
+package main
+
+import (
+	"fmt"
+)
+
+// This comment is associated with the hello constant.
+const hello = "Hello, World!" // line comment 1
+
+// This comment is associated with the foo variable.
+var foo = hello // line comment 2
+
+//@dump This comment is associated with the main function.
+func main() {
+	//@dump
+	fmt.Println(hello) // line comment 3
+	fmt.Println("a")
+	hello = b
+	c = hello
+	fmt.Println(foo) //@dump
+	//@dump
+}
+`
+	instrument(src)
+
+}
+
+func instrument(src string) {
+	// Create the AST by parsing src.
+	fset := token.NewFileSet() // positions are relative to fset
+	f, err := parser.ParseFile(fset, "test_program.go", src, parser.ParseComments)
+	if err != nil {
+		panic(err)
+	}
+
+	// Print the AST.
+	ast.Print(fset, f)
+
+	ast.Walk(new(ImportVisitor), f)
+	//printer.Fprint(os.Stdout, fset, f)
+
+}
+
+type ImportVisitor struct{}
+
+func (v *ImportVisitor) Visit(node ast.Node) (w ast.Visitor) {
+	switch t := node.(type) {
+	case *ast.FuncDecl:
+		t.Name = ast.NewIdent(strings.Title(t.Name.Name))
+	case *ast.Comment:
+		if strings.Contains(t.Text, "@dump") {
+			fmt.Println("dump encountered!")
+			fmt.Println(t.Text)
+
+		}
+	case *ast.AssignStmt:
+		fmt.Println(fmt.Sprintf("%v", t.Rhs[0]) + " -> " + fmt.Sprintf("%v", t.Lhs[0]))
+
+	}
+
+	return v
+}

### 2015-04-03 src/test_program.go

@@ -1,0 +1,23 @@
+// This is the package comment.
+package main
+
+import (
+	"fmt"
+)
+
+// This comment is associated with the hello constant.
+const hello = "Hello, World!" // line comment 1
+
+// This comment is associated with the foo variable.
+var foo = hello // line comment 2
+
+//@dump This comment is associated with the main function.
+func main() {
+	//@dump
+	fmt.Println(hello) // line comment 3
+	fmt.Println("a")
+	hello = b
+	c = hello
+	fmt.Println(foo) //@dump
+	//@dump
+}

### 2015-04-06 src/instrumenter.go
Adding Imports and Generated Codes

@@ -1,16 +1,18 @@
 package main
 
 import (
-	//"bytes"
+	"bytes"
 	"fmt"
 	"go/ast"
-	//"go/format"
 	"go/parser"
-	//"go/printer"
+	"go/printer"
 	"go/token"
-	//"os"
+	"os"
 	"strings"
 )
+
+var fset *token.FileSet
+var astFile *ast.File
 
 func main() {
 	src := `
@@ -20,6 +22,7 @@ package main
 import (
 	"fmt"
 )
+
 
 // This comment is associated with the hello constant.
 const hello = "Hello, World!" // line comment 1
@@ -38,22 +41,20 @@ func main() {
 	//@dump
 }
 `
-	instrument(src)
-
+	initializeInstrumenter(src)
+	addImports()
+	printer.Fprint(os.Stdout, fset, astFile)
 }
 
-func instrument(src string) {
+func initializeInstrumenter(src string) {
 	// Create the AST by parsing src.
-	fset := token.NewFileSet() // positions are relative to fset
-	f, err := parser.ParseFile(fset, "test_program.go", src, parser.ParseComments)
-	if err != nil {
-		panic(err)
-	}
+	fset = token.NewFileSet() // positions are relative to fset
+	astFile, _ = parser.ParseFile(fset, "test_program.go", src, parser.ParseComments)
 
 	// Print the AST.
-	ast.Print(fset, f)
+	//ast.Print(fset, astFile)
 
-	ast.Walk(new(ImportVisitor), f)
+	//ast.Walk(new(ImportVisitor), f)
 	//printer.Fprint(os.Stdout, fset, f)
 
 }
@@ -76,4 +77,105 @@ func (v *ImportVisitor) Visit(node ast.Node) (w ast.Visitor) {
 	}
 
 	return v
+}
+
+func GetAccessibleVarsInScope(lineNumber int) []string {
+	return nil
+}
+
+func GenerateDumpCode(vars []string, lineNumber int) string {
+	var buffer bytes.Buffer
+
+	// write vars' values
+	buffer.WriteString(fmt.Sprintf("vars%d := []interface{}{", lineNumber))
+
+	for i := 0; i < len(vars)-1; i++ {
+		buffer.WriteString(fmt.Sprintf("%s,", vars[i]))
+	}
+	buffer.WriteString(fmt.Sprintf("%s}\n", vars[len(vars)-1]))
+
+	// write vars' names
[…]

### 2015-04-23 Doc/introback.tex
Some Changes

@@
 for i := 1 to n do
-	send('Q',i)
+	send('Query',i)
 commit := decide()
@@
 	recv(buf,i)
-	if (buf == 'A')
-		commit := 'A'
+	if (buf == 'Abort')
+		commit := 'Abort'
 for i := 1 to n
@@
 recv(buf)
-if(buf == 'Q')
+if(buf == 'Query')
 	vote:= decide()
 	send(vote)
-if (vote == 'A')
-	commit = 'A'
+if (vote == 'Abort')
+	commit = 'Abort'
 else

### 2015-04-23 src/instrumenter/instrumenter.go

@@ -5,10 +5,10 @@ import (
 	"fmt"
 	"go/ast"
 	"go/parser"
-	"go/printer"
+	//"go/printer"
 	"go/token"
 	"golang.org/x/tools/go/ast/astutil"
-	"os"
+	//"os"
 	//"reflect"
 	"strings"
 )
@@ -17,74 +17,26 @@ var fset *token.FileSet
 var astFile *ast.File
 
 func main() {
-	//src := `
-	//// This is the package comment.
-	//package main
-
-	//import (
-	//"fmt"
-	//)
-
-	//// This comment is associated with the hello constant.
-	//const hello = "Hello, World!" // line comment 1
-
-	//// This comment is associated with the foo variable.
-	//var foo = hello // line comment 2
-
-	////@dump This comment is associated with the main function.
-	//func main() {
-	////@dump
-	//fmt.Println(hello) // line comment 3
-	//fmt.Println("a")
-	//hello = b
-	//c = hello
-	//fmt.Println(foo) //@dump
-	////@dump
-	//}
-	//`
-	src := `
-package main
-
-import "fmt"
-
-var gx = "Goodbye"
-
-func main() {
-	var z,x = "Hello"
-	fmt.Println(x)
-	x = "new"
-	fmt.Println(gx)
-	for {
-		var amt = 1
-		fmt.Println("inside incr")
-		return x + amt
-	}
-	fmt.Println(inc(2))
-	f()
-
-}
-
-func f() {
-	y := "Rocky"
-	fmt.Println(y)
-	fmt.Println(gx)
-}
-`
-
-	initializeInstrumenter(src)
+	initializeInstrumenter()
+	dumpNodes := GetDumpNodes()
 	addImports()
-	printer.Fprint(os.Stdout, fset, astFile)
+
+	for _, dumps := range dumpNodes {
+		fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+	}
+
+	//printer.Fprint(os.Stdout, fset, astFile)
 }
 
-func initializeInstrumenter(src string) {
+func initializeInstrumenter() {
 	// Create the AST by parsing src.
 	fset = token.NewFileSet() // positions are relative to fset
-	astFile, _ = parser.ParseFile(fset, "test_program.go", src, parser.ParseComments)
+	astFile, _ = parser.ParseFile(fset, "../TestPrograms/serverUDP.go", nil, parser.ParseComments)
 
 	// Print the AST.
[…]

### 2015-04-25 src/TestPrograms/assignment1.go
Test Programs

@@ -1,0 +1,47 @@
+package main
+
+import (
+	"fmt"
+	"net"
+	"os"
+)
+
+func main(){
+	
+	// check if the number of arguments passing to this program is correct
+	if len(os.Args) != 1 {
+		fmt.Println("program is supposed to have 0 arguments !\n")
+	}
+	
+	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
+	printErr(errR)
+	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
+	printErr(errL)
+	
+	conn, errDial := net.DialUDP("udp", lAddr, rAddr )
+	printErr(errDial)
+	
+	// sending UDP packet to specified address and port
+	msg := []byte("get me the message !")
+	_, errWrite := conn.Write(msg)
+	printErr(errWrite)
+	
+	// Reading the response message
+	var buf [1024]byte
+	n, errRead := conn.Read(buf[0:])
+	printErr(errRead)
+	//@dump
+	
+
+	fmt.Println(string(buf[:n]))
+	
+	os.Exit(0)
+}
+
+
+func printErr(err error){
+	if err != nil {
+		fmt.Println(err)
+		os.Exit(1)
+	}
+}

### 2015-04-25 src/TestPrograms/serverUDP.go

@@ -1,0 +1,45 @@
+package main
+
+import (
+	"fmt"
+	"net"
+	"time"
+)
+
+//@dump
+func main(){
+	conn , err := net.ListenPacket("udp",":8080")
+//	if err != nil {
+//		fmt.Println(err)
+//		os.Exit(1)
+//	}
+	printErr(err)
+	
+	for {
+		if err != nil {
+			printErr(err)
+			continue
+		}
+		handleConn(conn)
+		fmt.Println("some one connected!")
+		//@dump
+	}
+	conn.Close()
+	
+}
+
+func handleConn(conn net.PacketConn){
+	var buf [512]byte
+	
+	_, addr, err := conn.ReadFrom(buf[0:])
+	printErr(err)
+	msg := fmt.Sprintf("Hello There! time now is %s \n", time.Now().String())
+	conn.WriteTo([]byte(msg), addr)
+	//@dump
+}
+
+func printErr(err error){
+	if err != nil{
+		fmt.Println(err)
+	}
+}

### 2015-04-25 src/TestPrograms/test_program.go

@@ -1,0 +1,20 @@
+// This is the package comment.
+package main
+
+import (
+	"fmt"
+)
+
+const hello = "Hello, World!"
+
+var foo = hello // line comment 2
+
+func main() {
+	//@dump
+	fmt.Println(hello) // line comment 3
+	fmt.Println("a")
+	hello = b
+	c = hello
+	fmt.Println(foo) //@dump
+	//@dump
+}

### 2015-04-27 src/instrumenter/instrumenter.go
Dominance Graph and CFG

@@ -22,7 +22,7 @@ func main() {
 	addImports()
 
 	for _, dumps := range dumpNodes {
-		fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+		fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash)))
 	}
 
 	//printer.Fprint(os.Stdout, fset, astFile)
@@ -45,17 +45,18 @@ func initializeInstrumenter() {
 
 }
 
-func GetAccessibleVarsInScope(start int, file *ast.File) []string {
+func GetAccessibleVarsInScope(start int) []string {
+	fmt.Println(start)
 	var results []string
 
-	global_objs := file.Scope.Objects
+	global_objs := astFile.Scope.Objects
 
 	for identifier, _ := range global_objs {
 		results = append(results, fmt.Sprintf("%v, ", identifier))
 	}
 
-	filePos := fset.File(file.Package)
-	path, _ := astutil.PathEnclosingInterval(file, filePos.Pos(start), filePos.Pos(start+2))
+	filePos := fset.File(astFile.Package)
+	path, _ := astutil.PathEnclosingInterval(astFile, filePos.Pos(start), filePos.Pos(start+2))
 
 	for _, astnode := range path {
 

### 2015-04-27 src/programslicer/cfg/cfg.go

@@ -1,0 +1,494 @@
+// Copyright 2015 Auburn University. All rights reserved.
+// Use of this source code is governed by a BSD-style
+// license that can be found in the LICENSE file.
+
+// Package cfg provides intraprocedural control flow graphs (CFGs) with
+// statement-level granularity, i.e., CFGs whose nodes correspond 1-1 to the
+// Stmt nodes from an abstract syntax tree.
+package cfg
+
+import (
+	"fmt"
+	"go/ast"
+	"go/token"
+	"io"
+	"strings"
+
+	"golang.org/x/tools/go/ast/astutil"
+)
+
+// This package can be used to construct a control flow graph from an abstract syntax tree (go/ast).
+// This is done by traversing a list of statements (likely from a Block)
+// depth-first and creating an adjacency list, implemented as a map of Blocks.
+// Adjacent Blocks are stored as predecessors and successors separately for
+// control flow information. Any defers encountered while traversing the ast
+// will be added to a slice that can be accessed from CFG. Their behavior is such
+// that they may or may not be flowed to, potentially multiple times, after Exit.
+// This behavior is dependant upon in what control structure they were found,
+// i.e. if/for body may never be flowed to.
+
+// TODO(you): defers are lazily done currently. If needed, could likely use a more robust
+//  implementation wherein they are represented as a graph after Exit.
+// TODO(reed): closures, go func() ?
+
+// CFG defines a control flow graph with statement-level granularity, in which
+// there is a 1-1 correspondence between a Block in the CFG and an ast.Stmt.
+type CFG struct {
+	// Sentinel nodes for single-entry, single-exit CFG. Not in original AST.
+	Entry, Exit *ast.BadStmt
+	// All defers found in CFG, disjoint from Blocks. May be flowed to after Exit.
+	Defers     []*ast.DeferStmt
+	Blocks     map[ast.Stmt]*Block
[…]

### 2015-04-27 src/programslicer/cfg/dom.go

@@ -1,0 +1,333 @@
+// Copyright 2013 The Go Authors. All rights reserved.
+// Use of this source code is governed by a BSD-style
+// license that can be found in the LICENSE file.
+
+package cfg
+
+// This file defines algorithms related to dominance.
+
+// Dominator tree construction ----------------------------------------
+//
+// We use the algorithm described in Lengauer & Tarjan. 1979.  A fast
+// algorithm for finding dominators in a flowgraph.
+// http://doi.acm.org/10.1145/357062.357071
+//
+// We also apply the optimizations to SLT described in Georgiadis et
+// al, Finding Dominators in Practice, JGAA 2006,
+// http://jgaa.info/accepted/2006/GeorgiadisTarjanWerneck2006.10.1.pdf
+// to avoid the need for buckets of size > 1.
+
+import (
+	"bytes"
+	"fmt"
+	//"math/big"
+	//"os"
+	"go/token"
+	"golang.org/x/tools/go/ast/astutil"
+	"sort"
+)
+
+// Idom returns the block that immediately dominates b:
+// its parent in the dominator tree, if any.
+// Neither the entry node (b.Index==0) nor recover node
+// (b==b.Parent().Recover()) have a parent.
+//
+
+func (b *Block) String() string { return astutil.NodeDescription(b.Stmt) }
+
+func (b *Block) Idom() *Block { return b.dom.idom }
+
+// Dominees returns the list of blocks that b immediately dominates:
+// its children in the dominator tree.
+//
+func (b *Block) Dominees() []*Block { return b.dom.children }
+
+// Dominates reports whether b dominates c.
+func (b *Block) Dominates(c *Block) bool {
+	return b.dom.pre <= c.dom.pre && c.dom.post <= b.dom.post
+}
+
+type byDomPreorder []*Block
+
+func (a byDomPreorder) Len() int           { return len(a) }
+func (a byDomPreorder) Swap(i, j int)      { a[i], a[j] = a[j], a[i] }
+func (a byDomPreorder) Less(i, j int) bool { return a[i].dom.pre < a[j].dom.pre }
+
+// DomPreorder returns a new slice containing the blocks of f in
+// dominator tree preorder.
+//
[…]

### 2015-04-27 src/programslicer/programslicer.go

@@ -1,0 +1,66 @@
+// ProgramSlicer
+package main
+
+import (
+	"./cfg"
+	"fmt"
+	//"github.com/godoctor/godoctor/analysis/dataflow"
+	"bytes"
+	"go/ast"
+	"go/parser"
+	"go/token"
+)
+
+// Create CFG
+// For given graph compute dominator and post-dominators
+// Create Control Dependence Graph
+// Create Data Dependence Graph
+// Create Program Dependence Graph
+
+func main() {
+	src := `
+  package main
+
+  func foo(c int, nums []int) int {
+    //START
+    a := 1
+	b := 2
+	if a == 1 {
+		b = 1
+	} else {
+		b = 10
+	}
+	c = b + a
+    //END
+  }`
+
+	fset := token.NewFileSet()
+	f, err := parser.ParseFile(fset, "", src, 0)
+	if err != nil {
+		fmt.Println(err)
+		return
+	}
+
+	funcOne := f.Decls[0].(*ast.FuncDecl)
+	c := cfg.FromFunc(funcOne)
+	_ = c.GetBlocks() // for 100% coverage ;)
+	c.InitializeBlocks()
+	invC := c.InvertCFG()
+	var buf bytes.Buffer
+	invC.PrintDot(&buf, fset, func(s ast.Stmt) string {
+		if _, ok := s.(*ast.AssignStmt); ok {
+			return "!"
+		} else {
+			return ""
+		}
+	})
+	dot := buf.String()
+	fmt.Println(invC.BlockSlice)
+	cfg.BuildDomTree(invC)
+	cfg.PrintDomTreeDot(&buf, invC, fset)
+	dot = buf.String()
+
+	fmt.Println(dot)
+	//createMyCFG(c)
+
+}

### 2015-04-27 src/instrumenter/instrumenter.go
get used variables

@@ -11,10 +11,23 @@ import (
 	//"os"
 	//"reflect"
 	"strings"
+	"testing"
+
+	"golang.org/x/tools/go/loader"
+	"golang.org/x/tools/go/types"
+
+	"github.com/godoctor/godoctor/analysis/cfg"
+	"github.com/godoctor/godoctor/analysis/dataflow"
+)
+
+const (
+	START = 0
+	END   = 100000000 // if there's this many statements, may god have mercy on your soul
 )
 
 var fset *token.FileSet
 var astFile *ast.File
+var c *CFGWrapper
 
 func main() {
 	initializeInstrumenter()
@@ -22,7 +35,8 @@ func main() {
 	addImports()
 
 	for _, dumps := range dumpNodes {
-		fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+		//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+		fmt.Println(GetAccessedVarsInScope(dumps, astFile, c.f))
 	}
 
 	//printer.Fprint(os.Stdout, fset, astFile)
@@ -34,7 +48,13 @@ func initializeInstrumenter() {
 	astFile, _ = parser.ParseFile(fset, "../TestPrograms/serverUDP.go", nil, parser.ParseComments)
 
 	// Print the AST.
-	ast.Print(fset, astFile)
+
+	c = getWrapper(nil, "../TestPrograms/serverUDP.go")
+	//fset = c.fset
+
+	//astFile = c.f
+
+	//ast.Print(fset, astFile)
 
 	//collectVars(149, astFile)
 
@@ -42,6 +62,139 @@ func initializeInstrumenter() {
 
 	//ast.Walk(new(ImportVisitor), astFile)
 	//printer.Fprint(os.Stdout, fset, f)
+
+}
+
+func GetAccessedVarsInScope(dumpNode *ast.Comment, f *ast.File, g *ast.File) []string {
+	var results []string
+	//filePos := fset.File(file.Package)
+	//path, _ := astutil.PathEnclosingInterval(f, dumpNode.Pos(), dumpNode.End())
+	path2, _ := astutil.PathEnclosingInterval(g, dumpNode.Pos(), dumpNode.End())
+
+	var stmts []ast.Stmt
+
+	for _, astnode := range path2 {
+
+		funcDecl, ok := astnode.(*ast.FuncDecl)
+		if ok { // skip import decl if exists
+
[…]

### 2015-04-28 src/programslicer/cfg/cfg.go
CDG

@@ -43,13 +43,14 @@ type CFG struct {
 }
 
 type Block struct {
-	Index  int
-	Stmt   ast.Stmt
-	Preds  []ast.Stmt
-	Succs  []ast.Stmt
-	PredBs []*Block
-	SuccBs []*Block
-	dom    domInfo
+	Index      int
+	Stmt       ast.Stmt
+	Preds      []ast.Stmt
+	Succs      []ast.Stmt
+	PredBs     []*Block
+	SuccBs     []*Block
+	dom        domInfo
+	ControlDep []*Block
 }
 
 func (c *CFG) InitializeBlocks() {
@@ -143,6 +144,22 @@ splines="ortho";
 			fmt.Fprintf(f, "\t\"%s\" -> \"%s\"\n",
 				c.printVertex(v, fset, addl(v.Stmt)),
 				c.printVertex(c.Blocks[a], fset, addl(c.Blocks[a].Stmt)))
+		}
+	}
+	fmt.Fprintf(f, "}\n")
+}
+
+func (c *CFG) PrintControlDepDot(f io.Writer, fset *token.FileSet, addl func(n ast.Stmt) string) {
+	fmt.Fprintf(f, `digraph mgraph {
+mode="heir";
+splines="ortho";
+
+`)
+	for _, v := range c.Blocks {
+		for _, a := range v.ControlDep {
+			fmt.Fprintf(f, "\t\"%s\" -> \"%s\"\n",
+				c.printVertex(v, fset, addl(v.Stmt)),
+				c.printVertex(a, fset, addl(a.Stmt)))
 		}
 	}
 	fmt.Fprintf(f, "}\n")

### 2015-04-28 src/programslicer/cfg/dom.go

@@ -33,6 +33,45 @@ import (
 // (b==b.Parent().Recover()) have a parent.
 //
 
+func contains(s []*Block, e *Block) bool {
+	for _, a := range s {
+		if a == e {
+			return true
+		}
+	}
+	return false
+}
+
+//Consider all inverted CFG edges (x,c) such that x does not
+//dominate c (therefore, c is a branch node)
+//• Traverse the post‐dominator tree bottom‐up –n=x
+//– while (n != parent of c in the post‐dominator tree) • report that n is control dependent on c
+//• n = parent of n in the post‐dominator tree
+
+func (invC *CFG) FindControlDeps() {
+
+	// CFG is inverted
+	for _, x := range invC.BlockSlice {
+		for _, c := range x.SuccBs {
+			if !x.Dominates(c) {
+				n := x
+				for n != c.dom.idom && n != nil {
+					n.ControlDep = append(n.ControlDep, c)
+					n = n.dom.idom
+				}
+			}
+		}
+	}
+
+}
+
+func (c *CFG) BuildPostDomTree() *CFG {
+	c.InitializeBlocks()
+	invC := c.InvertCFG()
+	BuildDomTree(invC)
+	return invC
+}
+
 func (b *Block) String() string { return astutil.NodeDescription(b.Stmt) }
 
 func (b *Block) Idom() *Block { return b.dom.idom }

### 2015-04-28 src/programslicer/cfg/cfg.go
DDG

@@ -51,6 +51,7 @@ type Block struct {
 	SuccBs     []*Block
 	dom        domInfo
 	ControlDep []*Block
+	DataDep    []*Block
 }
 
 func (c *CFG) InitializeBlocks() {
@@ -157,6 +158,22 @@ splines="ortho";
 `)
 	for _, v := range c.Blocks {
 		for _, a := range v.ControlDep {
+			fmt.Fprintf(f, "\t\"%s\" -> \"%s\"\n",
+				c.printVertex(v, fset, addl(v.Stmt)),
+				c.printVertex(a, fset, addl(a.Stmt)))
+		}
+	}
+	fmt.Fprintf(f, "}\n")
+}
+
+func (c *CFG) PrintDataDepDot(f io.Writer, fset *token.FileSet, addl func(n ast.Stmt) string) {
+	fmt.Fprintf(f, `digraph mgraph {
+mode="heir";
+splines="ortho";
+
+`)
+	for _, v := range c.Blocks {
+		for _, a := range v.DataDep {
 			fmt.Fprintf(f, "\t\"%s\" -> \"%s\"\n",
 				c.printVertex(v, fset, addl(v.Stmt)),
 				c.printVertex(a, fset, addl(a.Stmt)))

### 2015-04-28 src/programslicer/programslicer.go

@@ -1,66 +1,0 @@
-// ProgramSlicer
-package main
-
-import (
-	"./cfg"
-	"fmt"
-	//"github.com/godoctor/godoctor/analysis/dataflow"
-	"bytes"
-	"go/ast"
-	"go/parser"
-	"go/token"
-)
-
-// Create CFG
-// For given graph compute dominator and post-dominators
-// Create Control Dependence Graph
-// Create Data Dependence Graph
-// Create Program Dependence Graph
-
-func main() {
-	src := `
-  package main
-
-  func foo(c int, nums []int) int {
-    //START
-    a := 1
-	b := 2
-	if a == 1 {
-		b = 1
-	} else {
-		b = 10
-	}
-	c = b + a
-    //END
-  }`
-
-	fset := token.NewFileSet()
-	f, err := parser.ParseFile(fset, "", src, 0)
-	if err != nil {
-		fmt.Println(err)
-		return
-	}
-
-	funcOne := f.Decls[0].(*ast.FuncDecl)
-	c := cfg.FromFunc(funcOne)
-	_ = c.GetBlocks() // for 100% coverage ;)
-	c.InitializeBlocks()
-	invC := c.InvertCFG()
-	var buf bytes.Buffer
-	invC.PrintDot(&buf, fset, func(s ast.Stmt) string {
-		if _, ok := s.(*ast.AssignStmt); ok {
-			return "!"
-		} else {
-			return ""
-		}
-	})
-	dot := buf.String()
-	fmt.Println(invC.BlockSlice)
-	cfg.BuildDomTree(invC)
-	cfg.PrintDomTreeDot(&buf, invC, fset)
-	dot = buf.String()
-
-	fmt.Println(dot)
-	//createMyCFG(c)
-
-}

### 2015-04-28 src/instrumenter/instrumenter.go
send and receive

@@ -39,8 +39,7 @@ func main() {
 		fmt.Println(GetAccessedVarsInScope(dumps, astFile, c.f))
 
 	}
-
-	//printer.Fprint(os.Stdout, fset, astFile)
+	fmt.Println(detectSendReceive(astFile))
 }
 
 func initializeInstrumenter() {
@@ -55,7 +54,7 @@ func initializeInstrumenter() {
 
 	//astFile = c.f
 
-	//ast.Print(fset, astFile)
+	ast.Print(fset, astFile)
 
 	//collectVars(149, astFile)
 
@@ -64,6 +63,32 @@ func initializeInstrumenter() {
 	//ast.Walk(new(ImportVisitor), astFile)
 	//printer.Fprint(os.Stdout, fset, f)
 
+}
+
+func detectSendReceive(f *ast.File) []*ast.Node {
+	var results []*ast.Node
+	ast.Inspect(f, func(n ast.Node) bool {
+		switch x := n.(type) {
+		case *ast.CallExpr:
+			switch y := x.Fun.(type) {
+			case *ast.SelectorExpr:
+				left, ok := y.X.(*ast.Ident)
+				if ok && left.Name == "conn" && y.Sel.Name == "ReadFrom" || y.Sel.Name == "WriteTo" {
+
+					fmt.Println(left.Name, y.Sel.Name)
+
+					results = append(results, &n)
+
+				}
+
+			}
+
+			return true
+		}
+
+		return true
+	})
+	return results
 }
 
 func GetAccessedVarsInScope(dumpNode *ast.Comment, f *ast.File, g *ast.File) []string {

### 2015-04-28 src/programslicer/cfg/cfg.go
Program Slicer Added

@@ -43,15 +43,17 @@ type CFG struct {
 }
 
 type Block struct {
-	Index      int
-	Stmt       ast.Stmt
-	Preds      []ast.Stmt
-	Succs      []ast.Stmt
-	PredBs     []*Block
-	SuccBs     []*Block
-	dom        domInfo
-	ControlDep []*Block
-	DataDep    []*Block
+	Index        int
+	Stmt         ast.Stmt
+	Preds        []ast.Stmt
+	Succs        []ast.Stmt
+	PredBs       []*Block
+	SuccBs       []*Block
+	dom          domInfo
+	ControlDep   []*Block
+	ControlDepee []*Block
+	DataDep      []*Block
+	DataDepee    []*Block
 }
 
 func (c *CFG) InitializeBlocks() {
@@ -94,6 +96,8 @@ func (c *CFG) InvertCFG() *CFG {
 		invB.Stmt = b.Stmt
 		invB.Preds = b.Succs
 		invB.Succs = b.Preds
+		invB.DataDep = b.DataDep
+		invB.DataDepee = b.DataDepee
 		invCFG.Blocks[invB.Stmt] = invB
 	}
 	invCFG.InitializeBlocks()

### 2015-04-28 src/programslicer/cfg/dom.go

@@ -57,6 +57,7 @@ func (invC *CFG) FindControlDeps() {
 				n := x
 				for n != c.dom.idom && n != nil {
 					n.ControlDep = append(n.ControlDep, c)
+					c.ControlDepee = append(c.ControlDepee, n)
 					n = n.dom.idom
 				}
 			}

### 2015-04-28 src/programslicer/dataflow/reaching.go

@@ -62,6 +62,7 @@ func CreateDataDepGraph(cfg *cfg.CFG, info *loader.PackageInfo) {
 			defVars := defs(defStmt, info)
 			if intersectDefUse(defVars, useVars) {
 				useB.DataDep = append(useB.DataDep, defB)
+				defB.DataDepee = append(defB.DataDepee, useB)
 			}
 
 		}

### 2015-04-28 src/programslicer/programslicer.go

@@ -1,0 +1,211 @@
+// ProgramSlicer
+package main
+
+import (
+	"./cfg"
+	"./dataflow"
+	"bytes"
+	"fmt"
+	"go/ast"
+	"go/token"
+	"golang.org/x/tools/go/loader"
+)
+
+// Create CFG
+// For given graph compute dominator and post-dominators
+// Create Control Dependence Graph
+// Create Data Dependence Graph
+// Create Program Dependence Graph
+
+func ComputeForwardSlice(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo, fset *token.FileSet) []ast.Stmt {
+
+	var slice []ast.Stmt
+	dataflow.CreateDataDepGraph(cfg, info)
+	invC := cfg.BuildPostDomTree()
+	invC.FindControlDeps()
+
+	var buf bytes.Buffer
+	invC.PrintControlDepDot(&buf, fset, func(s ast.Stmt) string {
+		if _, ok := s.(*ast.AssignStmt); ok {
+			return "!"
+		} else {
+			return ""
+		}
+	})
+
+	dot := buf.String()
+	fmt.Println(dot)
+
+	visited := make(map[ast.Stmt]bool)
+	queue := make([]ast.Stmt, 0)
+	queue = append(queue, start)
+	visited[start] = true
+	slice = append(slice, start)
+	for len(queue) != 0 {
+		uStmt := queue[0]
+		queue = queue[1:]
+		u := invC.Blocks[uStmt]
+
+		//debugging
+		fmt.Println("visiting ")
+		fmt.Println(fset.Position(u.Stmt.Pos()).Line)
+		fmt.Println("control deps :")
+		for _, v := range u.ControlDepee {
+
+			fmt.Println(fset.Position(v.Stmt.Pos()).Line)
+			if !visited[v.Stmt] {
+				visited[v.Stmt] = true
+				queue = append(queue, v.Stmt)
+				slice = append(slice, v.Stmt)
+			}
+		}
+		fmt.Println("data deps :")
+		for _, v := range u.DataDepee {
+			fmt.Println(fset.Position(v.Stmt.Pos()).Line)
+			if !visited[v.Stmt] {
+				visited[v.Stmt] = true
+				queue = append(queue, v.Stmt)
+				slice = append(slice, v.Stmt)
+			}
+		}
+	}
+
+	return slice
+}
+
[…]

### 2015-04-29 src/instrumenter/instrumenter.go
start on report

@@ -22,7 +22,7 @@ import (
 
 const (
 	START = 0
-	END   = 100000000 // if there's this many statements, may god have mercy on your soul
+	END   = 100000000
 )
 
 var fset *token.FileSet
@@ -43,20 +43,16 @@ func main() {
 }
 
 func initializeInstrumenter() {
+	src_location := "../TestPrograms/serverUDP.go"
 	// Create the AST by parsing src.
 	fset = token.NewFileSet() // positions are relative to fset
-	astFile, _ = parser.ParseFile(fset, "../TestPrograms/serverUDP.go", nil, parser.ParseComments)
+	astFile, _ = parser.ParseFile(fset, src_location, nil, parser.ParseComments)
 
 	// Print the AST.
 
-	c = getWrapper(nil, "../TestPrograms/serverUDP.go")
-	//fset = c.fset
-
-	//astFile = c.f
+	c = getWrapper(nil, src_location)
 
 	ast.Print(fset, astFile)
-
-	//collectVars(149, astFile)
 
 	//fmt.Println(pathStr)
 
@@ -74,15 +70,10 @@ func detectSendReceive(f *ast.File) []*ast.Node {
 			case *ast.SelectorExpr:
 				left, ok := y.X.(*ast.Ident)
 				if ok && left.Name == "conn" && y.Sel.Name == "ReadFrom" || y.Sel.Name == "WriteTo" {
-
 					fmt.Println(left.Name, y.Sel.Name)
-
 					results = append(results, &n)
-
 				}
-
 			}
-
 			return true
 		}
 

### 2015-04-29 src/programslicer/programslicer.go
Get Affected Vars

@@ -9,6 +9,7 @@ import (
 	"go/ast"
 	"go/token"
 	"golang.org/x/tools/go/loader"
+	"golang.org/x/tools/go/types"
 )
 
 // Create CFG
@@ -71,6 +72,32 @@ func ComputeForwardSlice(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo,
 	}
 
 	return slice
+}
+
+func GetBackwardAffectedVariables(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo, fset *token.FileSet) []*types.Var {
+
+	stmts := ComputeBackwardSlice(start, cfg, info, fset)
+	defs, _ := dataflow.ReferencedVars(stmts, info)
+
+	var affectedVars []*types.Var
+	for def := range defs {
+		affectedVars = append(affectedVars, def)
+	}
+
+	return affectedVars
+}
+
+func GetForwardAffectedVariables(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo, fset *token.FileSet) []*types.Var {
+
+	stmts := ComputeForwardSlice(start, cfg, info, fset)
+	defs, _ := dataflow.ReferencedVars(stmts, info)
+
+	var affectedVars []*types.Var
+	for def := range defs {
+		affectedVars = append(affectedVars, def)
+	}
+
+	return affectedVars
 }
 
 func ComputeBackwardSlice(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo, fset *token.FileSet) []ast.Stmt {
@@ -201,11 +228,12 @@ func main() {
 
 	ast.Print(prog.Fset, funcOne.Body.List)
 	fmt.Println("computing slice ...")
-	slice := ComputeForwardSlice(funcOne.Body.List[0], c, prog.Created[0], prog.Fset)
+	slice := GetForwardAffectedVariables(funcOne.Body.List[1], c, prog.Created[0], prog.Fset)
 	fmt.Println("slice")
 	fmt.Println(len(slice))
 	for _, s := range slice {
-		fmt.Println(prog.Fset.Position(s.Pos()).Line)
+		//fmt.Println(prog.Fset.Position(s.Pos()).Line)
+		fmt.Println(s.Name())
 	}
 
 }

### 2015-04-29 src/instrumenter/instrumenter.go
replacing with dump code

@@ -5,11 +5,12 @@ import (
 	"fmt"
 	"go/ast"
 	"go/parser"
-	//"go/printer"
+	"go/printer"
 	"go/token"
 	"golang.org/x/tools/go/ast/astutil"
 	//"os"
 	//"reflect"
+	"regexp"
 	"strings"
 	"testing"
 
@@ -30,19 +31,34 @@ var astFile *ast.File
 var c *CFGWrapper
 
 func main() {
-	initializeInstrumenter()
+	source := initializeInstrumenter()
 	dumpNodes := GetDumpNodes()
 	addImports()
 
-	for _, dumps := range dumpNodes {
+	var generated_code []string
+	for _, dump := range dumpNodes {
 		//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
-		fmt.Println(GetAccessedVarsInScope(dumps, astFile, c.f))
+		fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
+		line := c.fset.Position(dump.Pos()).Line
+		fmt.Println(line)
+		generated_code = append(generated_code, GenerateDumpCode(GetAccessedVarsInScope(dump, astFile, c.f), line))
 
 	}
+	count := 0
+	rp := regexp.MustCompile("\\/\\/@dump")
+	transformed := rp.ReplaceAllStringFunc(source, func(s string) string {
+		replacement := generated_code[count]
+		count++
+		return replacement
+	})
+
+	fmt.Println(transformed)
+
 	fmt.Println(detectSendReceive(astFile))
+
 }
 
-func initializeInstrumenter() {
+func initializeInstrumenter() string {
 	src_location := "../TestPrograms/serverUDP.go"
 	// Create the AST by parsing src.
 	fset = token.NewFileSet() // positions are relative to fset
@@ -51,8 +67,20 @@ func initializeInstrumenter() {
 	// Print the AST.
 
 	c = getWrapper(nil, src_location)
-
 	ast.Print(fset, astFile)
+
+	//var buf bytes.Buffer
+	//if err := format.Node(&buf, fset, f); err != nil {
+	//return nil, err
+	//}
+	//return buf.Bytes(), nil
+
+	var buf bytes.Buffer
+	printer.Fprint(&buf, fset, astFile)
+
+	s := buf.String()
+
+	return s
 
 	//fmt.Println(pathStr)
 
@@ -282,6 +310,10 @@ func GetDumpNodes() []*ast.Comment {
 
[…]

### 2015-04-29 src/instrumenter/instrumenter.go
rewriting all parts

@@ -33,14 +33,13 @@ var c *CFGWrapper
 func main() {
 	source := initializeInstrumenter()
 	dumpNodes := GetDumpNodes()
-	addImports()
 
 	var generated_code []string
 	for _, dump := range dumpNodes {
 		//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
-		fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
+		//fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
 		line := c.fset.Position(dump.Pos()).Line
-		fmt.Println(line)
+		//fmt.Println(line)
 		generated_code = append(generated_code, GenerateDumpCode(GetAccessedVarsInScope(dump, astFile, c.f), line))
 
 	}
@@ -52,9 +51,9 @@ func main() {
 		return replacement
 	})
 
+	transformed = transformed + "\n" + extra_code
 	fmt.Println(transformed)
-
-	fmt.Println(detectSendReceive(astFile))
+	//fmt.Println(detectSendReceive(astFile))
 
 }
 
@@ -67,7 +66,9 @@ func initializeInstrumenter() string {
 	// Print the AST.
 
 	c = getWrapper(nil, src_location)
-	ast.Print(fset, astFile)
+	//ast.Print(fset, astFile)
+
+	addImports()
 
 	//var buf bytes.Buffer
 	//if err := format.Node(&buf, fset, f); err != nil {
@@ -98,7 +99,7 @@ func detectSendReceive(f *ast.File) []*ast.Node {
 			case *ast.SelectorExpr:
 				left, ok := y.X.(*ast.Ident)
 				if ok && left.Name == "conn" && y.Sel.Name == "ReadFrom" || y.Sel.Name == "WriteTo" {
-					fmt.Println(left.Name, y.Sel.Name)
+					//fmt.Println(left.Name, y.Sel.Name)
 					results = append(results, &n)
 				}
 			}
@@ -332,58 +333,56 @@ func GenerateDumpCode(vars []string, lineNumber int) string {
 	}
 	buffer.WriteString(fmt.Sprintf("\"%s\"}\n", vars[len(vars)-1]))
 
-	buffer.WriteString(fmt.Sprintf("point%d := createPoint(vars%d, varNames%d, %d)\n", lineNumber, lineNumber, lineNumber, lineNumber))
[…]

### 2015-04-30 Doc/approach.tex
doc template change
Program Slicer Described

--- 2015-03-04 Doc/approach.tex
@@
 number of program points and huge number of variables in a relatively
-large program this approach is not scalable. So we propose two main
+large program this approach is not scalable and also we can end up inferring incorrect invariants that are hold by accident. So we propose two main
 optimizations to reduce the number of program point, variable value
@@
 developer, vector clocks will be used to partially order annotation
-pairs in the two programs. This will also help to invalidate
-annotations inserted at irrelevant locations by the developer.
+pairs in the two programs.% This will also help to invalidate
+% annotations inserted at irrelevant locations by the developer.
 
-\subsection{Dataflow analysis for Go programs}
+\subsection{Data and Control Flow analysis for Go programs}
 
 Even at interesting program points, variable space that need to be
-captured is very large. So only the variables that were affected by
+captured is very large and also we want to filter out irrelevant invariants by only considering variables that affect each other for invariant detection phase.
+So only the variables that were affected by
 the communication with other nodes need to be identified. To detect
@@
 For example using a forward flow analysis on Listing~\ref{lst:node1} we can say that \texttt{sum} variable at line 4 and line 5 is affected by the \texttt{buf} variable at line 1.
-But currently there are no data flow analysis
-frameworks specifically for Go programs.
+But currently there are no data or control flow analysis
+frameworks for Go programs.
 
-So we are planning to do a dynamic dataflow analysis which consists of follwing steps:
-\begin{itemize}
-\item Instrumenting variable declarations and assignments at the run time
-\item Collecting execution traces of each of these statements by runnning test suites
-\item Doing a forward flow analysis using the collected traces
-\end{itemize}
+\subsubsection{Go Program Slicer}
 
-This dynamic analysis approach was chosen because it gives information about the actual execution and therefore is more accurate.
+``A program slice consists of the parts of a program that (potentially) affect the values computed at some point of interest"\cite{Tip}.
+For example figure \ref{Fig:backslice} illustrates an example Go program and its computed backward slice from line 11, the sliced program only contains statements that affect value of variables used at line 11 (i.e.
+product).
+To identify variables affected by the communication with other nodes we computed the forward slice from receive message functions and computed backward slice from send message functions.
+To compute these forward and backward slices we used the approach first proposed by Ottenstein and Ottenstein \cite{PDG}, which used Program Dependence Graph (PDG) and computed slices by checking the reachability of nodes in this graph.
+PDG captures both control dependency and data dependency of the program, in fact PDG is computed by combining both Data Dependence Graph and Control Dependence Graph (CDG) of a program.
+Figure \ref{fig:pdg} illustrates our approach to compute PDG.
+First, we computed the Control Flow Graph (CFG) of the program, then from the reversed CFG we computed the post-dominance tree.
+The Dominance tree is computed by the algorithm proposed by Lengauer and Tarjan in \cite{Dom}.
+In the next step we computed the CDG from post-dominance tree.
+To compute Data Dependence Graph, first we computed the reaching definitions by solving dataflow equations\cite{dragonbook} and then used $(Def,Use)$ pair to compute the data dependency between associated statements and form Data Dependence Graph.
+We combined Data and Control Dependence Graphs to compute the PDG.
+Having the PDG of the program we checked the reachability of nodes in PDG starting from start node to compute forward and backward slices.
+
+\begin{figure}
+  \includegraphics[width=\columnwidth,scale=0.5]{images/PDG-approach.png}
+  \caption{Our approach to compute program dependence graph}
+  \label{fig:pdg}
+\end{figure}
+
+\begin{figure}
+\begin{subfigure}[b]{\linewidth}
+\centering
+ \begin{lstlisting}[]
+	recv(n)
+	i := 1
+	sum := 0
+	product := 1
+	for i <= n {
+		sum := sum + i
+		product := product * i
+		i := i + 1
+	}
+	send(sum)
+	send(product)
+\end{lstlisting}
+        \vspace{-2mm}
+                \caption{A Go Program}
+        \end{subfigure}
+
+\begin{subfigure}[b]{\linewidth}
+\centering
+\begin{lstlisting}[]
+	recv(n)
+	i := 1
+
+	product := 1
+	for i <= n {
+
+		product := product * i
+		i := i + 1
+	}
+
+	send(product) // backward slice from here
+\end{lstlisting}
+        \vspace{-2mm}
+                \caption{Go program backward sliced at line 10}
+%                \label{Fig:refactored}
+        \end{subfigure}
+                        \caption{Backward slice of a Go program \cite{Tip} }
+                \label{Fig:backslice}
+\end{figure}
+
+%So we are planning to do a dynamic dataflow analysis which consists of following steps:
+%\begin{itemize}
+%\item Instrumenting variable declarations and assignments at the run time
+%\item Collecting execution traces of each of these statements by runnning test suites
+%\item Doing a forward flow analysis using the collected traces
+%\end{itemize}
+
+%This dynamic analysis approach was chosen because it gives information about the actual execution and therefore is more accurate.
 And also compared to using a static analysis-based approach, this approach makes it easier to handle Go language-specific constructs like channels which are used share data between goroutines.
@@
 
+Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
+\begin{itemize}
+\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
+\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be dumped at each point is determined
+\item Program is instrumented to dump selected variable values, their type and current vector clock at the annotated program points at run time
+\item Based on the vector clock of each log, logs are paired to each other and combined variable values of two logs is fed to the daikon in its specific format.
+%For this we are hoping to use static analysis libraries
+%available under Go-lang Parse package and tools\cite{static_golang} which provide
+%support for Identifier resolution, Type information, Call graph
+%navigation and Channel peers (send $\leftrightarrow$ receive)
+%identification.
+%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
+%\item Forward flow analysis is done on the collected traces
+%\item Using the results of the previous step, variables contributing to distributed state is identified.
+%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
+%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
+\end{itemize}
+
 \begin{figure}
@@
 \end{figure}
+
+% \section{Timeline}
+
+% Following is the planned milestones and estimated timeline for the project completion.
+
+% \begin{description}
+%   \item[2/10:] Proposal Draft Submission
+%   \item[3/3:] Proposal Submission
+%   \item[3/7:] Finalizing the design, Familirization with required tools (Daikon, Go source analysis tools)
+%   \item[3/14:] Implementation - Go program instrumentation to handle annotations and dumping state
+%   \item[3/21:] Implementation - Dynamic Forward Analysis for Go programs
+%   \item[3/28:] Implementation - Vector clocks integration and end-to-end working analysis
+%   \item[4/4:] Evaluation - Inferring invariants in test programs
+%   \item[4/7:] Project Presentation
+%   \item[4/16:] Project Code and Report Submission
+% \end{description}

### 2015-04-30 Doc/evalrelate.tex
doc template change
Program Slicer Described
Some Notes On Implementation

@@
-\section{Evaluation Methodology}
+\subsection{Implementation}
+
+\subsubsection{Program Slicer}
+
+Go program slicer is built on top of CFG and reaching definitions computed as part of Go Doctor (The Golang Refactoring Engine) project \cite{godoctor}.
+Also, some code snippets from Go static single-assignment (SSA) package \cite{ssa} is used to compute dominance tree from CFG.
+After building PDG, reachability of nodes from start node is determined via a breadth-first search on the graph.
+
+\section{Results}
 We will implement our approach in a tool in Go programming language.

### 2015-04-30 Doc/introback.tex
Program Slicer Described

@@
+\section{Abstract}
 \section{Introduction}
 
-Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or network fail, this means that there are many corner cases that developers should consider when building the system.
+Building a reliable distributed system is a difficult task, since distributed system should continue operating even when components or the network fail, this means that there are many corner cases that developers should consider when building a system.
 Building such
-a reliable and dependable system is not possible without thorough testing of the system.
-However, testing a distributed system is a much more difficult task because it is much harder to test components of a distributed system in isolation.
+a reliable and dependable system is not possible without thorough testing.
+However, testing a distributed system is a difficult task because it is hard to test components of a distributed system in isolation.
 There are many
-failure scenarios that distributed system should handle and these scenarios should be tested as well.
-In some cases reproducing the failures is a difficult task e.g.
-degrading network performance for test purposes.
-Many bugs turn out to be heisenbugs in distributed
-system which are hard to reproduce and detect.
-For testing and debugging distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and looking for incidents that system does not behave as
+failure scenarios that a distributed system should handle and these scenarios should be tested as well.
+In some cases reproducing the failures is a difficult task e.g., degrading network performance for test purposes.
+Many bugs turn out to be heisenbugs in a distributed
+system which are hard to reproduce and debug.
+Debugging and testing distributed systems is hard because a fault in a single node is not confined to that node, instead, it may cause an error in another node.
+In fact errors in distributed system should be defined on global state of the system and not on a single node.
+This also makes program comprehension of distributed systems a difficult task, since the developer needs to comprehend interaction of different nodes as well as logic of each node.
+
+To test and debug distributed systems, developers and testers have to spend a considerable amount of time inspecting logs of the system manually and look for incidents the system does not behave as 
 expected.
-One alternative to this laborious approach is to define invariants for system's expected behaviour and check the software traces against these invariants.
+One alternative to this laborious approach is to define invariants for a system's expected behaviour and check the software traces against these invariants.
 This approach is considerably easier than the former but as the system gets larger and more
 complex, providing invariants manually becomes more difficult.
-
-Testing distributed systems is hard because a fault in a single node does not confine to that node, instead, it may cause an error in another node.
-In fact errors in distributed system should be defined on global state of the system and not on a single node.
-In this work we
-assume that state of each node is comprised of its variables.
-Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node.
-We refer to set of distributed
-state variables of all nodes as distributed state of the system.
+In this work, we automate the process of defining invariants for systems by inferring likely invariants of distributed systems from run time execution of systems.
+We define an invariant of distributed systems as a property that holds at a certain consistent cut across multiple nodes in distributed state of a distributed program.
+These inferred invariants can ease many programming tasks, such as program comprehension, bug prevention, debugging, verification and testing.
+Inferred invariants can show specification of systems,  act as documentation and help program comprehension.
+They can be checked after each modification to source code to make sure that invariants of the system that implies its correctness are not violated, thus helping bug prevention.
+Even if the bugs get into the system, these invariants can help debugging by locating the points in program that they got violated.
+Moreover, they can be written in form of assertions and be used for automated test generation.
+%Ernst et al \cite{ernst2007daikon} define a program invariant as ``a property that holds at a certain point or points in a program".
 
 %The most challenging part of this work is to find valid snapshots of distributed states for the system. 
-
-\section{Motivating Example}
-For motivation example, consider pseudo-two-phase-commit protocol of figure \ref{lst:2pc}.
-In this protocol coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
+Consider pseudo-two-phase-commit protocol in figure \ref{lst:2pc}.
+In this protocol the coordinator first queries other nodes for their vote and if all nodes including the coordinator vote ``Commit" then the coordinator sends ``Commit", otherwise it sends ``Abort" to all other nodes.
 At the end of this protocol all nodes should either commit or abort .
-In order to verify that this algorithm is working correctly, developers can examine inferred invariants of the protocol execution and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value and this property should be inferred by executing the protocol).
-We use daikon \cite{ernst2001dynamically} to infer invariants between variables so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
+To verify that this algorithm is correct, developers can examine inferred invariants of the protocol execution and inspect if these inferred invariants match expected behaviour of the system (In this case commit value of all nodes should have the same value i.e., $coordinator.commit$ = $replica_i .commit$ for each replica).
 
@@
 \end{lstlisting}
-\begin{lstlisting}[caption={Coordinator Code}]
+\begin{lstlisting}[caption={Replica Code}]
 recv(buf)
@@
 \end{lstlisting}
-\caption{Pseudo two phase commit code for coordinator and cohorts}
+\caption{Pseudo two phase commit code for coordinator and replicas}
 \label{lst:2pc}
@@
 
+In this work we 
+assume that state of each node is comprised of its variables.
+Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node.
+We refer to set of distributed
+state variables of all nodes as distributed state of the system.
+We use daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
+
 \section{Background}
 
-Invariants are properties that should hold in  certain points in program.
-Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is a open problem.
+Invariants are properties that should hold in certain points in a program.
+Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is an open problem.
 To infer invariants in a distributed system we should have global snapshots (log of variables) of the system.
 However, not every snapshot of the system is a valid one.
-Mattern introduced the notion of cut and consistent cut as snapshot and valid snapshots of a system.
-In \cite{mattern1989virtual} he also proposed an algorithm to find consistent cuts.
+Mandy and Lamport introduced the notion of cut and consistent cut as snapshot and valid snapshots of a system.
+In \cite{mattern1989virtual}, Mattern proposed an algorithm to find consistent cuts.
 The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes consists a significant portion of distributed state of that node.

### 2015-04-30 Doc/approach.tex
Background revisited

@@
 The ultimate goal of this project is to infer invariants in a
-distributed system. For the scope of this project we will consider a
+distributed system. For this project we consider a
 system with 2 nodes. Before inferring invariants we need to identify
@@
 the equality between elements in each pair \texttt{(a,first),
-(b,second),(sum,result)} and also the properites: \texttt{(result = a
+(b,second),(sum,result)} and also the properties: \texttt{(result = a
 + b)} and \texttt{(sum = first + second)}.
@@
 
-The naive approach for inferring these invariants will be to dump all
-state varaible values at all program points and feed them to an
-invariant detector like daikon\cite{ernst2007daikon}. But given the
+As mentioned earlier, the naive approach for inferring these invariants will be to dump all
+state variable values at all program points and feed them to an
+invariant detector like Daikon\cite{ernst2007daikon}. But given the
 number of program points and huge number of variables in a relatively
-large program this approach is not scalable and also we can end up inferring incorrect invariants that are hold by accident. So we propose two main
+large program this approach is not scalable. Moreover, it can result in inferring incorrect invariants that are hold by accident. So we propose two main
 optimizations to reduce the number of program point, variable value
@@
 statements which will write the values of variable to a file when the
-program reaches that point in the runtime.
-
-Since there can be multiple points annotated in a program by a
+program reaches that point in the runtime. Since there can be multiple points annotated in a program by a
 developer, vector clocks will be used to partially order annotation
@@
 So only the variables that were affected by
-the communication with other nodes need to be identified. To detect
-these variables, some form of dataflow analysis is required. This
-includes the dataflow of the distributed system as a whole and also in
-a single program.
-For example using a forward flow analysis on Listing~\ref{lst:node1} we can say that \texttt{sum} variable at line 4 and line 5 is affected by the \texttt{buf} variable at line 1.
-But currently there are no data or control flow analysis
-frameworks for Go programs.
+the communication with other nodes need to be identified (distributed state variables).  To detect
+these variables, some form of data and control flow analysis is required.
+For example using a backward flow analysis on Listing~\ref{lst:node1} we can say that \texttt{sum} variable at line 4 and line 5 is affected by the \texttt{buf} variable and receive function at line 1.
+Note that \texttt{sum} variable is part of distributed state of the system, since its value is affected by a receive function and affects a send function, so it is possibly affected and affects variables in other nodes of the system (here it is affected variables \texttt{a} and \texttt{b} and affects \texttt{result} in Node 0).
+To compute these distributed state variables, we developed a Go program slicer which we explain in the following section.
 
@@
 product).
-To identify variables affected by the communication with other nodes we computed the forward slice from receive message functions and computed backward slice from send message functions.
+To identify variables affected by the communication with other nodes we computed the forward slice from receive message functions and computed backward slice from send message functions and determined the variables assigned in these sliced statements.
 To compute these forward and backward slices we used the approach first proposed by Ottenstein and Ottenstein \cite{PDG}, which used Program Dependence Graph (PDG) and computed slices by checking the reachability of nodes in this graph.
 PDG captures both control dependency and data dependency of the program, in fact PDG is computed by combining both Data Dependence Graph and Control Dependence Graph (CDG) of a program.
+For example figure \ref{fig:expdg} depicts the PDG of example program of figure \ref{Fig:backslice}.
 Figure \ref{fig:pdg} illustrates our approach to compute PDG.
 First, we computed the Control Flow Graph (CFG) of the program, then from the reversed CFG we computed the post-dominance tree.
-The Dominance tree is computed by the algorithm proposed by Lengauer and Tarjan in \cite{Dom}.
+The Dominance tree is computed by the algorithm proposed by Lengauer and Tarjan \cite{Dom}.
 In the next step we computed the CDG from post-dominance tree.
@@
 Having the PDG of the program we checked the reachability of nodes in PDG starting from start node to compute forward and backward slices.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth,scale=0.5]{images/PDG-approach.png}
-  \caption{Our approach to compute program dependence graph}
-  \label{fig:pdg}
-\end{figure}
+For example, In PDG of figure \ref{fig:expdg} thick lines are control dependence edges and thin lines are data dependence edges, starting from \texttt{send(product)} node and going backward shaded nodes are reachable, so the shaded nodes are in backward slice of \texttt{send(product)} statement.
 
@@
                 \label{Fig:backslice}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth,scale=0.5]{images/PDG-approach.png}
+  \caption{Our approach to compute program dependence graph}
+  \label{fig:pdg}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth,scale=0.5]{images/pdg.png}
+  \caption{Program Dependence Graph of Example Program in Figure \ref{Fig:backslice}}
+  \label{fig:expdg}
 \end{figure}

### 2015-04-30 src/TestPrograms/assignment1.go
modified programs to have vclocks

@@ -1,45 +1,45 @@
 package main
 
 import (
+	"../govec"
 	"fmt"
 	"net"
 	"os"
 )
 
-func main(){
-	
+var Logger *govec.GoLog
+
+func main() {
+	Logger = govec.Initialize("Client", "testclient.log")
 	// check if the number of arguments passing to this program is correct
 	if len(os.Args) != 1 {
 		fmt.Println("program is supposed to have 0 arguments !\n")
 	}
-	
+
 	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
 	printErr(errR)
 	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
 	printErr(errL)
-	
-	conn, errDial := net.DialUDP("udp", lAddr, rAddr )
+
+	conn, errDial := net.DialUDP("udp", lAddr, rAddr)
 	printErr(errDial)
-	
+
 	// sending UDP packet to specified address and port
-	msg := []byte("get me the message !")
-	_, errWrite := conn.Write(msg)
+	msg := "get me the message !"
+	_, errWrite := conn.Write(Logger.PrepareSend("Asking time", []byte(msg)))
 	printErr(errWrite)
-	
+
 	// Reading the response message
 	var buf [1024]byte
 	n, errRead := conn.Read(buf[0:])
 	printErr(errRead)
 	//@dump
-	
+	fmt.Println(string(Logger.UnpackReceive("Received", buf[:n])))
 
-	fmt.Println(string(buf[:n]))
-	
 	os.Exit(0)
 }
 
-
-func printErr(err error){
+func printErr(err error) {
 	if err != nil {
 		fmt.Println(err)
 		os.Exit(1)

### 2015-04-30 src/TestPrograms/serverUDP.go

@@ -1,20 +1,24 @@
 package main
 
 import (
+	"../govec"
 	"fmt"
 	"net"
 	"time"
 )
 
+var Logger *govec.GoLog
+
 //@dump
-func main(){
-	conn , err := net.ListenPacket("udp",":8080")
-//	if err != nil {
-//		fmt.Println(err)
-//		os.Exit(1)
-//	}
+func main() {
+	Logger = govec.Initialize("Server", "testlog.log")
+	conn, err := net.ListenPacket("udp", ":8080")
+	//	if err != nil {
+	//		fmt.Println(err)
+	//		os.Exit(1)
+	//	}
 	printErr(err)
-	
+
 	for {
 		if err != nil {
 			printErr(err)
@@ -25,21 +29,22 @@ func main(){
 		//@dump
 	}
 	conn.Close()
-	
+
 }
 
-func handleConn(conn net.PacketConn){
+func handleConn(conn net.PacketConn) {
 	var buf [512]byte
-	
+
 	_, addr, err := conn.ReadFrom(buf[0:])
+	Logger.UnpackReceive("Received", buf[0:])
 	printErr(err)
 	msg := fmt.Sprintf("Hello There! time now is %s \n", time.Now().String())
-	conn.WriteTo([]byte(msg), addr)
+	conn.WriteTo(Logger.PrepareSend("Sending", []byte(msg)), addr)
 	//@dump
 }
 
-func printErr(err error){
-	if err != nil{
+func printErr(err error) {
+	if err != nil {
 		fmt.Println(err)
 	}
 }

### 2015-04-30 Doc/introback.tex

@@
 state variables of all nodes as distributed state of the system.
-We use daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
+We use Daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
 
@@
 Invariants are properties that should hold in certain points in a program.
-Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is an open problem.
-To infer invariants in a distributed system we should have global snapshots (log of variables) of the system.
+Although previous works \cite{ernst2001dynamically} showed that invariant inference is feasible in sequential programs, inferring invariants in a distributed system poses unique challenges and still is an open problem.To infer invariants in a distributed system we should have global snapshots (log of variables) of the system.
 However, not every snapshot of the system is a valid one.
@@
 In \cite{mattern1989virtual}, Mattern proposed an algorithm to find consistent cuts.
+We used vector clocks \cite{vectorclock} to partially order snapshots of the nodes in our system and form consistent cuts.
 The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes consists a significant portion of distributed state of that node.
-We use dynamic data flow analysis to detect the distributed state of the system.
-We also use vector clocks to partially order snapshots of the nodes in our system and form consistent cuts.
+We use static data and control flow analysis to detect the distributed state of the system.
+To do so we computed the forward and backward slice of the program  \cite{programslice} from communication points in the program, such as receive and send functions, and determined list of variables whose values are affected by a receive function or can affect values that are sent by a send function.
+By doing so, we identified the variables that contribute to interactions between nodes, possibly affect values of variables in other nodes, hence form the distributed state of the program.
 
-Our approach is to automatically infer invariants that may exist in distributed state of our system.
-To this end, we execute distributed programs by running the test cases and dynamically select a set of variables in each node that likely represent the distributed state
-across our distributed nodes.
-We do so with dynamic data flow analysis of variables and selecting those that are affected by a send or receive operation.
-Finally we use Daikon to infer invariants among our distributed state variables.
-\\ \\
 We can view our approach as an optimization.
-The naive approach to solve inference problem is to log all of the variables at each instruction execution and give all consistent cuts of the system to daikon to infer invariants between the variables.
-However, this naive approach is not efficient at all, if a total number of n instruction is executed during a run by all nodes in the system and on average we have m variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up finding many false positives (invariants that hold by accident and are not meaningful).
-Our approach only logs variables that an invariant might exist between them by using data flow analysis and finding group of variables (across the nodes) which affect each other.
+The naive approach to solve inference problem is to log all of the variables at each instruction execution and give all consistent cuts of the system to a invariant detector tool to infer invariants between the variables.
+However, this naive approach is not efficient at all, if a total number of $n$ instruction is executed during a run by all nodes in the system and on average we have $m$ variables for each node, we should log $n*m$ variables but many of these variables are local to one node and are not affected by other nodes, so we may even end up finding many false positives (invariants that hold by accident and are not meaningful).
+Our approach only logs variables that an invariant might exist between them by using data and control flow analysis and finding group of variables (across the nodes) which affect each other.
 Another optimization that our approach does is that instead of logging the variables at each instruction, we only log them at consistent cuts annotated by developers.
-Based on our observation some must-hold invariants can be violated for small amount of time (e.g.
-execution time of several instructions) until systems goes to a stable state, so we decided to give developers responsibility to decide at which points in program invariants should hold and can be checked by annotating the code.
+Based on our observation some must-hold invariants can be violated for small amount of time (e.g., execution time of several instructions) until systems goes to a stable state, so we decided to give developers responsibility to decide at which points in program invariants should hold and can be checked, by annotating the code.
 By this approach we improve usefulness of our tool for developers.
 Another approach can be inferring the invariants from logs of the system, our approach removes the burden from developers to decide which portion of each node's state needs to be logged.
-We automatically infer variables that are likely to have invariants between them with data flow analysis.
+We automatically infer the variables that are likely to have invariants between them with data and control flow analysis.

### 2015-05-01 src/LogMerger.go
progress

@@ -9,15 +9,18 @@ import (
 )
 
 func main() {
-	log1 := readLog("log1.txt")
-	log2 := readLog("log2.txt")
+	log1 := readLog("TestPrograms/log_client.txt")
+	log2 := readLog("TestPrograms/log_server.txt")
+	fmt.Println(log1[0].vectorClock)
+	fmt.Println(log2[0].vectorClock)
 	mergedLog := mergeLogs(log1, log2)
+	writeLogToFile(mergedLog)
 
 }
 
 func writeLogToFile(log []Point) {
 
-	file, err := os.Create("daikonLog.txt")
+	file, _ := os.Create("daikonLog.txt")
 
 	mapOfPoints := createMapOfLogsForEachPoint(log)
 	writeDeclaration(file, mapOfPoints)
@@ -37,7 +40,7 @@ func createMapOfLogsForEachPoint(log []Point) map[string][]Point {
 
 func writeDeclaration(file *os.File, mapOfPoints map[string][]Point) {
 
-	for k, v := range mapOfPoints {
+	for _, v := range mapOfPoints {
 		point := v[0]
 		file.WriteString(fmt.Sprintf("ppt p-%s:::%s\n", point.LineNumber, point.LineNumber))
 		file.WriteString(fmt.Sprintf("ppt-type point\n"))
@@ -77,6 +80,7 @@ func mergeLogs(log1, log2 []Point) []Point {
 	for i := 0; i < len(log1); i++ {
 
 		matchedPoints := findMatch(log1[i], log2)
+		fmt.Println(matchedPoints)
 		for j := 0; j < len(matchedPoints); j++ {
 			mergedPoints = append(mergedPoints, mergePoints(matchedPoints[j], log1[i]))
 		}
@@ -105,6 +109,7 @@ func mergePoints(p1, p2 Point) Point {
 func findMatch(point Point, log []Point) []Point {
 	matched := make([]Point, 0)
 	pVClock, err := vclock.FromBytes(point.vectorClock)
+	fmt.Println(pVClock)
 	printErr(err)
 	for i := 0; i < len(log); i++ {
 
@@ -133,6 +138,8 @@ func readLog(filePath string) []Point {
 		e = decoder.Decode(&decodedPoint)
 		if e == nil {
 			pointArray = append(pointArray, decodedPoint)
+		} else {
+			fmt.Println(e)
 		}
 	}
 

### 2015-05-01 src/TestPrograms/assignment1_mod.go

@@ -1,0 +1,97 @@
+package main
+
+import (
+	"../govec"
+	"encoding/gob"
+	"fmt"
+	"net"
+	"os"
+	"reflect"
+)
+
+func main() {
+	InstrumenterInit()
+	Logger = govec.Initialize("Client", "testclient.log")
+
+	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
+	printErr(errR)
+	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
+	printErr(errL)
+
+	conn, errDial := net.DialUDP("udp", lAddr, rAddr)
+	printErr(errDial)
+
+	// sending UDP packet to specified address and port
+	msg := "get me the message !"
+	_, errWrite := conn.Write(Logger.PrepareSend("Asking time", []byte(msg)))
+	printErr(errWrite)
+
+	// Reading the response message
+	var buf [1024]byte
+	n, errRead := conn.Read(buf[0:])
+	printErr(errRead)
+	vars30 := []interface{}{conn, buf, errRead, rAddr, errDial, msg, Logger, errWrite, errR, errL, lAddr}
+	varsName30 := []string{"conn", "buf", "errRead", "rAddr", "errDial", "msg", "Logger", "errWrite", "errR", "errL", "lAddr"}
+	point30 := createPoint(vars30, varsName30, 30)
+	encoder.Encode(point30)
+	fmt.Println(string(Logger.UnpackReceive("Received", buf[:n])))
+
+	os.Exit(0)
+}
+
+func printErr(err error) {
+	if err != nil {
+		fmt.Println(err)
+		os.Exit(1)
+	}
+}
+
+var Logger *govec.GoLog
+
+var encoder *gob.Encoder
+
+func InstrumenterInit() {
+	fileW, _ := os.Create("log_client.txt")
+	encoder = gob.NewEncoder(fileW)
+}
+
+func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
+
+	length := len(varNames)
+	dumps := make([]NameValuePair, 0)
+	for i := 0; i < length; i++ {
+
+		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
+			var dump NameValuePair
+			dump.VarName = varNames[i]
+			dump.Value = vars[i]
[…]

### 2015-05-01 src/TestPrograms/serverudp_mod.go

@@ -1,0 +1,105 @@
+package main
+
+import (
+	"../govec"
+	"encoding/gob"
+	"fmt"
+	"net"
+	"os"
+	"reflect"
+	"time"
+)
+
+func main() {
+	InstrumenterInit()
+	Logger = govec.Initialize("Server", "testlog.log")
+	conn, err := net.ListenPacket("udp", ":8080")
+	//	if err != nil {
+	//		fmt.Println(err)
+	//		os.Exit(1)
+	//	}
+	printErr(err)
+
+	for {
+		if err != nil {
+			printErr(err)
+			continue
+		}
+		handleConn(conn)
+		fmt.Println("some one connected!")
+		vars27 := []interface{}{err, conn}
+		varsName27 := []string{"err", "conn"}
+		point27 := createPoint(vars27, varsName27, 27)
+		encoder.Encode(point27)
+	}
+	conn.Close()
+
+}
+
+func handleConn(conn net.PacketConn) {
+	var buf [512]byte
+
+	_, addr, err := conn.ReadFrom(buf[0:])
+	Logger.UnpackReceive("Received", buf[0:])
+	printErr(err)
+	msg := fmt.Sprintf("Hello There! time now is %s \n", time.Now().String())
+	conn.WriteTo(Logger.PrepareSend("Sending", []byte(msg)), addr)
+	vars41 := []interface{}{conn, buf, Logger, err, msg, addr}
+	varsName41 := []string{"conn", "buf", "Logger", "err", "msg", "addr"}
+	point41 := createPoint(vars41, varsName41, 41)
+	encoder.Encode(point41)
+}
+
+func printErr(err error) {
+	if err != nil {
+		fmt.Println(err)
+	}
+}
+
+var Logger *govec.GoLog
+
+var encoder *gob.Encoder
+
+func InstrumenterInit() {
+	fileW, _ := os.Create("log_server.txt")
+	encoder = gob.NewEncoder(fileW)
+}
+
+func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
+
+	length := len(varNames)
+	dumps := make([]NameValuePair, 0)
+	for i := 0; i < length; i++ {
+		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
+			var dump NameValuePair
+			dump.VarName = varNames[i]
+			dump.Value = vars[i]
[…]

### 2015-05-01 src/instrumenter/instrumenter.go

@@ -58,7 +58,7 @@ func main() {
 }
 
 func initializeInstrumenter() string {
-	src_location := "../TestPrograms/serverUDP.go"
+	src_location := "../TestPrograms/assignment1.go"
 	// Create the AST by parsing src.
 	fset = token.NewFileSet() // positions are relative to fset
 	astFile, _ = parser.ParseFile(fset, src_location, nil, parser.ParseComments)
@@ -346,7 +346,7 @@ func InstrumenterInit() {
 	fileW, _ := os.Create("log.txt")
 	encoder = gob.NewEncoder(fileW)
 }
-var logger *govec.GoLog
+
 func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 
 	length := len(varNames)
@@ -356,7 +356,7 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 		dumps[i].Value = vars[i]
 		dumps[i].Type = reflect.TypeOf(vars[i]).String()
 	}
-	point := Point{dumps, lineNumber, logger.GetCurrentVC()}
+	point := Point{dumps, lineNumber, Logger.GetCurrentVC()}
 
 	return point
 }
@@ -382,7 +382,7 @@ func (p Point) String() string {
 }`
 
 func addImports() {
-	packagesToImport := []string{"\"encoding/gob\"", "\"os\"", "\"reflect\"", "\"../govec\""}
+	packagesToImport := []string{"\"encoding/gob\"", "\"os\"", "\"reflect\""}
 	im := ImportAdder{packagesToImport}
 	ast.Walk(im, astFile)
 	ast.SortImports(fset, astFile)

### 2015-05-01 src/LogMerger.go
progress.

@@ -11,8 +11,8 @@ import (
 func main() {
 	log1 := readLog("TestPrograms/log_client.txt")
 	log2 := readLog("TestPrograms/log_server.txt")
-	fmt.Println(log1[0].vectorClock)
-	fmt.Println(log2[0].vectorClock)
+	fmt.Println(log1[0].VectorClock)
+	fmt.Println(log2[0].VectorClock)
 	mergedLog := mergeLogs(log1, log2)
 	writeLogToFile(mergedLog)
 
@@ -94,13 +94,13 @@ func mergePoints(p1, p2 Point) Point {
 	var mergedPoint Point
 	mergedPoint.Dump = append(p1.Dump, p2.Dump...)
 	mergedPoint.LineNumber = p1.LineNumber + "-" + p2.LineNumber
-	pVClock1, err := vclock.FromBytes(p1.vectorClock)
+	pVClock1, err := vclock.FromBytes(p1.VectorClock)
 	printErr(err)
-	pVClock2, err2 := vclock.FromBytes(p2.vectorClock)
+	pVClock2, err2 := vclock.FromBytes(p2.VectorClock)
 	printErr(err2)
 	temp := pVClock1.Copy()
 	temp.Merge(pVClock2)
-	mergedPoint.vectorClock = temp.Bytes()
+	mergedPoint.VectorClock = temp.Bytes()
 
 	return mergedPoint
 
@@ -108,12 +108,12 @@ func mergePoints(p1, p2 Point) Point {
 
 func findMatch(point Point, log []Point) []Point {
 	matched := make([]Point, 0)
-	pVClock, err := vclock.FromBytes(point.vectorClock)
+	pVClock, err := vclock.FromBytes(point.VectorClock)
 	fmt.Println(pVClock)
 	printErr(err)
 	for i := 0; i < len(log); i++ {
 
-		otherVClock, err2 := vclock.FromBytes(log[i].vectorClock)
+		otherVClock, err2 := vclock.FromBytes(log[i].VectorClock)
 		printErr(err2)
 		if pVClock.Matches(otherVClock) {
 			matched = append(matched, log[i])
@@ -155,7 +155,7 @@ func printErr(err error) {
 type Point struct {
 	Dump        []NameValuePair
 	LineNumber  string
-	vectorClock []byte
+	VectorClock []byte
 }
 
 type NameValuePair struct {

### 2015-05-01 src/TestPrograms/assignment1_mod.go

@@ -71,7 +71,7 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 	}
 	fmt.Println(Logger.GetCurrentVC())
 	point := Point{dumps, string(lineNumber), Logger.GetCurrentVC()}
-	fmt.Println(point.vectorClock)
+	fmt.Println(point.VectorClock)
 
 	return point
 }
@@ -79,7 +79,7 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 type Point struct {
 	Dump        []NameValuePair
 	LineNumber  string
-	vectorClock []byte
+	VectorClock []byte
 }
 
 type NameValuePair struct {

### 2015-05-01 src/TestPrograms/serverudp_mod.go

@@ -87,7 +87,7 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 type Point struct {
 	Dump        []NameValuePair
 	LineNumber  string
-	vectorClock []byte
+	VectorClock []byte
 }
 
 type NameValuePair struct {

### 2015-05-01 Doc/approach.tex
Make it wider

@@
 \begin{figure}
+\begin{minipage}{.45\textwidth}
 \begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
@@
 \end{lstlisting}
-\end{figure}
-
-\begin{figure}
+\end{minipage}\hfill
+\begin{minipage}{.45\textwidth}
 \begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 1}, label=lst:node1]
@@
 \end{lstlisting}
+\end{minipage}\hfill
 \end{figure}
 
-As mentioned earlier, the naive approach for inferring these invariants will be to dump all
-state variable values at all program points and feed them to an
-invariant detector like Daikon\cite{ernst2007daikon}. But given the
-number of program points and huge number of variables in a relatively
-large program this approach is not scalable. Moreover, it can result in inferring incorrect invariants that are hold by accident. So we propose two main
-optimizations to reduce the number of program point, variable value
-combinations.
+%As mentioned earlier, the naive approach for inferring these invariants will be to dump all
+%state variable values at all program points and feed them to an
+%invariant detector like Daikon\cite{ernst2007daikon}. But given the
+%number of program points and huge number of variables in a relatively
+%large program this approach is not scalable. Moreover, it can result in inferring incorrect invariants that are hold by accident. So we propose two main
+%optimizations to reduce the number of program point, variable value
+%combinations.
+
+Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
+\begin{itemize}
+\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
+\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be collected at each point is determined
+\item Program is instrumented to log selected variable values, their type and current vector clock at the annotated program points at run time
+\item Program is executed by test cases or appropriate inputs and logs of variables are collected
+\item Based on the vector clock of each log, logs are paired to each other
+\item Combined variable values of two logs is fed to the daikon in its specific format.
+%For this we are hoping to use static analysis libraries
+%available under Go-lang Parse package and tools\cite{static_golang} which provide
+%support for Identifier resolution, Type information, Call graph
+%navigation and Channel peers (send $\leftrightarrow$ receive)
+%identification.
+%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
+%\item Forward flow analysis is done on the collected traces
+%\item Using the results of the previous step, variables contributing to distributed state is identified.
+%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
+%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
+\end{itemize}
+In each of the following sections we explain each step in detail.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{go_flow.png}
+  \caption{Flow of the invariant inference of Go programs}
+  \label{fig:go_flow}
+\end{figure}
 
@@
 \begin{figure}
+\begin{minipage}{.45\textwidth}
 \begin{subfigure}[b]{\linewidth}
@@
         \end{subfigure}
-
+\end{minipage}\hfill
+\begin{minipage}{.45\textwidth}
 \begin{subfigure}[b]{\linewidth}
@@
         \end{subfigure}
+        \end{minipage}\hfill
                         \caption{Backward slice of a Go program \cite{Tip} }
@@
 \end{figure}
+
+%\begin{figure}
+%\begin{subfigure}[b]{\linewidth}
+%\centering
+% \begin{lstlisting}[]
+%	recv(n)
+%	i := 1
+%	sum := 0
+%	product := 1
+%	for i <= n {
+%		sum := sum + i
+%		product := product * i
+%		i := i + 1
+%	}
+%	send(sum)
+%	send(product)
+%\end{lstlisting}
+%        \vspace{-2mm}
+%                \caption{A Go Program}
+%        \end{subfigure}
+%
+%\begin{subfigure}[b]{\linewidth}
+%\centering
+%\begin{lstlisting}[]
+%	recv(n)
+%	i := 1
+%
+%	product := 1
+%	for i <= n {
+%		
+%		product := product * i
+%		i := i + 1
+%	}
+%	
+%	send(product) // backward slice from here
+%\end{lstlisting}
+%        \vspace{-2mm}
+%                \caption{Go program backward sliced at line 10}
+%%                \label{Fig:refactored}
+%        \end{subfigure}
+%                        \caption{Backward slice of a Go program \cite{Tip} }
+%                \label{Fig:backslice}
+%\end{figure}
 
@@
   \includegraphics[width=\columnwidth,scale=0.5]{images/pdg.png}
-  \caption{Program Dependence Graph of Example Program in Figure \ref{Fig:backslice}}
+  \caption{Program Dependence Graph of Example Program in Figure \ref{Fig:backslice} \cite{Tip}}
   \label{fig:expdg}
 \end{figure}
+
+\subsection{Matching Logs with Vector Clocks}
 
@@
 
-Overall execution flow of the analysis is illustrated in Figure~\ref{fig:go_flow} and works as follows:
-\begin{itemize}
-\item Developer annotates interesting program points in the Go program which will be used as states for mining invariants.
-\item Program Dependence Graph is computed and based on the location of send, receive and developer annotated points, set of variables that contribute to distributed state of the system and thus should be dumped at each point is determined
-\item Program is instrumented to dump selected variable values, their type and current vector clock at the annotated program points at run time
-\item Based on the vector clock of each log, logs are paired to each other and combined variable values of two logs is fed to the daikon in its specific format.
-%For this we are hoping to use static analysis libraries
-%available under Go-lang Parse package and tools\cite{static_golang} which provide
-%support for Identifier resolution, Type information, Call graph
-%navigation and Channel peers (send $\leftrightarrow$ receive)
-%identification.
-%\item Then as the first step in the analysis phase, this instrumented program is executed using the test suites and program traces are collected.
-%\item Forward flow analysis is done on the collected traces
-%\item Using the results of the previous step, variables contributing to distributed state is identified.
-%\item From the dumped variable values at annotated program points (after multiple executions), only the values of variables chosen in the previous step are selected.
-%\item Selected variable values belonging to 2 distinct annotated program points in the 2 nodes are fed to Daikon for inferring invariants.
-\end{itemize}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{go_flow.pdf}
-  \caption{Flow of the invariant inference of Go programs}
-  \label{fig:go_flow}
-\end{figure}
-
 % \section{Timeline}

### 2015-05-01 src/LogMerger.go
some more progress

@@ -6,16 +6,28 @@ import (
 	"encoding/gob"
 	"fmt"
 	"os"
+	//"reflect"
 )
 
 func main() {
 	log1 := readLog("TestPrograms/log_client.txt")
 	log2 := readLog("TestPrograms/log_server.txt")
-	fmt.Println(log1[0].VectorClock)
-	fmt.Println(log2[0].VectorClock)
+	addNodeName("client.", log1)
+	addNodeName("server.", log2)
+	fmt.Println(log1[0])
+	fmt.Println(log2[0])
 	mergedLog := mergeLogs(log1, log2)
 	writeLogToFile(mergedLog)
 
+}
+
+func addNodeName(name string, logs []Point) {
+	for i := range logs {
+		for j := range logs[i].Dump {
+			//fmt.Println(dp.VarName)
+			logs[i].Dump[j].VarName = name + logs[i].Dump[j].VarName
+		}
+	}
 }
 
 func writeLogToFile(log []Point) {
@@ -66,7 +78,12 @@ func writeValues(file *os.File, log []Point) {
 		for i := range point.Dump {
 			variable := point.Dump[i]
 			file.WriteString(fmt.Sprintf("%s\n", variable.VarName))
-			file.WriteString(fmt.Sprintf("%s\n", variable.Value))
+			if variable.Type == "int" {
+				file.WriteString(fmt.Sprintf("%d\n", variable.Value))
+			} else {
+				file.WriteString(fmt.Sprintf("%s\n", variable.Value))
+			}
+
 			file.WriteString(fmt.Sprintf("1\n"))
 
 		}

### 2015-05-01 src/TestPrograms/assignment1.go

@@ -7,14 +7,8 @@ import (
 	"os"
 )
 
-var Logger *govec.GoLog
-
 func main() {
 	Logger = govec.Initialize("Client", "testclient.log")
-	// check if the number of arguments passing to this program is correct
-	if len(os.Args) != 1 {
-		fmt.Println("program is supposed to have 0 arguments !\n")
-	}
 
 	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
 	printErr(errR)
@@ -33,8 +27,9 @@ func main() {
 	var buf [1024]byte
 	n, errRead := conn.Read(buf[0:])
 	printErr(errRead)
+	incoming_msg := string(Logger.UnpackReceive("Received", buf[:n]))
+	fmt.Println(">>>" + incoming_msg)
 	//@dump
-	fmt.Println(string(Logger.UnpackReceive("Received", buf[:n])))
 
 	os.Exit(0)
 }
@@ -45,3 +40,5 @@ func printErr(err error) {
 		os.Exit(1)
 	}
 }
+
+var Logger *govec.GoLog

### 2015-05-01 src/TestPrograms/assignment1_mod2.go

@@ -11,7 +11,8 @@ import (
 )
 
 func main() {
-	InstrumenterInit()
+ InstrumenterInit()
+
 	Logger = govec.Initialize("Client", "testclient.log")
 
 	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
@@ -31,13 +32,12 @@ func main() {
 	var buf [1024]byte
 	n, errRead := conn.Read(buf[0:])
 	printErr(errRead)
-	incoming_msg := string(buf[:n])
-	fmt.Println(incoming_msg)
-	vars30 := []interface{}{incoming_msg, conn, buf, errRead, rAddr, errDial, msg, Logger, errWrite, errR, errL, lAddr}
-	varsName30 := []string{"incoming_msg", "conn", "buf", "errRead", "rAddr", "errDial", "msg", "Logger", "errWrite", "errR", "errL", "lAddr"}
-	point30 := createPoint(vars30, varsName30, 30)
-	encoder.Encode(point30)
-	fmt.Println(string(Logger.UnpackReceive("Received", buf[:n])))
+	incoming_msg := string(Logger.UnpackReceive("Received", buf[:n]))
+	fmt.Println(">>>" + incoming_msg)
+	vars32 := []interface{}{conn,buf,n,errL,errDial,Logger,msg,errWrite,errRead,incoming_msg,errR,lAddr,rAddr}
+varsName32 := []string{"conn","buf","n","errL","errDial","Logger","msg","errWrite","errRead","incoming_msg","errR","lAddr","rAddr"}
+point32 := createPoint(vars32, varsName32, 32)
+encoder.Encode(point32)
 
 	os.Exit(0)
 }
@@ -50,6 +50,8 @@ func printErr(err error) {
 }
 
 var Logger *govec.GoLog
+
+
 
 var encoder *gob.Encoder
 
@@ -66,7 +68,7 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 
 		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
 			var dump NameValuePair
-			dump.VarName = "client." + varNames[i]
+			dump.VarName = varNames[i]
 			dump.Value = vars[i]
 			dump.Type = reflect.TypeOf(vars[i]).String()
 			dumps = append(dumps, dump)
[…]

### 2015-05-01 src/TestPrograms/serverUDP.go

@@ -7,8 +7,6 @@ import (
 	"time"
 )
 
-var Logger *govec.GoLog
-
 //@dump
 func main() {
 	Logger = govec.Initialize("Server", "testlog.log")
@@ -48,3 +46,5 @@ func printErr(err error) {
 		fmt.Println(err)
 	}
 }
+
+var Logger *govec.GoLog

### 2015-05-01 src/TestPrograms/serverUDP_mod.go

@@ -1,0 +1,98 @@
+package main
+
+import (
+	//"./govec"
+	"bytes"
+	"encoding/gob"
+	"fmt"
+	"net"
+	"os"
+	"reflect"
+	"time"
+)
+
+var encoder gob.Encoder
+
+func InstrumenterInit() {
+	fileW, _ := os.Create("log.txt")
+	encoder = gob.NewEncoder(fileW)
+}
+
+var logger *govec.GoLog
+
+func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
+
+	length := len(varNames)
+	dumps := make([]NameValuePair, length)
+	for i := 0; i < length; i++ {
+		dumps[i].VarName = varNames[i]
+		dumps[i].Value = vars[i]
+		dumps[i].Type = reflect.TypeOf(vars[i]).String()
+	}
+	point := Point{dumps, lineNumber, logger.currentVC}
+
+	return point
+}
+
+type Point struct {
+	Dump        []NameValuePair
+	LineNumber  int
+	vectorClock []byte
+}
+
+type NameValuePair struct {
+	VarName string
+	Value   interface{}
+	Type    string
+}
+
+func (nvp NameValuePair) String() string {
+	return fmt.Sprintf("(%s,%s,%s)", nvp.VarName, nvp.Value, nvp.Type)
+}
+
+func (p Point) String() string {
+	return fmt.Sprintf("%d : %s", p.LineNumber, p.Dump)
+}
+
+func main() {
+	conn, err := net.ListenPacket("udp", ":8080")
+	//	if err != nil {
+	//		fmt.Println(err)
+	//		os.Exit(1)
+	//	}
+	printErr(err)
+
+	for {
+		if err != nil {
+			printErr(err)
+			continue
+		}
+		handleConn(conn)
+		fmt.Println("some one connected!")
+		vars25 := []interface{}{err, conn}
+		varsName25 := []string{"err", "conn"}
+		point25 := createPoint(vars25, varsName25, 25)
+		encoder.Encode(point25)
+	}
+	conn.Close()
+
+}
+
+func handleConn(conn net.PacketConn) {
+	var buf [512]byte
+
+	_, addr, err := conn.ReadFrom(buf[0:])
+	printErr(err)
+	msg := fmt.Sprintf("Hello There! time now is %s \n", time.Now().String())
+	conn.WriteTo([]byte(msg), addr)
[…]

### 2015-05-01 src/TestPrograms/serverudp_mod.go

@@ -7,6 +7,7 @@ import (
 	"net"
 	"os"
 	"reflect"
+	"strconv"
 	"time"
 )
 
@@ -72,14 +73,14 @@ func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 	for i := 0; i < length; i++ {
 		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
 			var dump NameValuePair
-			dump.VarName = varNames[i]
+			dump.VarName = "server." + varNames[i]
 			dump.Value = vars[i]
 			dump.Type = reflect.TypeOf(vars[i]).String()
 			dumps = append(dumps, dump)
 		}
 	}
 	fmt.Println(Logger.GetCurrentVC())
-	point := Point{dumps, string(lineNumber), Logger.GetCurrentVC()}
+	point := Point{dumps, strconv.Itoa(lineNumber), Logger.GetCurrentVC()}
 
 	return point
 }

### 2015-05-01 src/TestPrograms/serverudp_mod2.go

@@ -8,48 +8,60 @@ import (
 	"os"
 	"reflect"
 	"strconv"
+	"time"
 )
 
+
 func main() {
-	InstrumenterInit()
-	Logger = govec.Initialize("Client", "testclient.log")
+ InstrumenterInit()
 
-	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
-	printErr(errR)
-	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
-	printErr(errL)
+	Logger = govec.Initialize("Server", "testlog.log")
+	conn, err := net.ListenPacket("udp", ":8080")
+	//	if err != nil {
+	//		fmt.Println(err)
+	//		os.Exit(1)
+	//	}
+	printErr(err)
 
-	conn, errDial := net.DialUDP("udp", lAddr, rAddr)
-	printErr(errDial)
+	for {
+		if err != nil {
+			printErr(err)
+			continue
+		}
+		handleConn(conn)
+		fmt.Println("some one connected!")
+		vars27 := []interface{}{err,conn}
+varsName27 := []string{"err","conn"}
+point27 := createPoint(vars27, varsName27, 27)
+encoder.Encode(point27)
+	}
+	conn.Close()
 
-	// sending UDP packet to specified address and port
-	msg := "get me the message !"
-	_, errWrite := conn.Write(Logger.PrepareSend("Asking time", []byte(msg)))
-	printErr(errWrite)
+}
 
-	// Reading the response message
-	var buf [1024]byte
-	n, errRead := conn.Read(buf[0:])
-	printErr(errRead)
-	incoming_msg := string(buf[:n])
-	fmt.Println(incoming_msg)
-	vars30 := []interface{}{incoming_msg, conn, buf, errRead, rAddr, errDial, msg, Logger, errWrite, errR, errL, lAddr}
-	varsName30 := []string{"incoming_msg", "conn", "buf", "errRead", "rAddr", "errDial", "msg", "Logger", "errWrite", "errR", "errL", "lAddr"}
-	point30 := createPoint(vars30, varsName30, 30)
-	encoder.Encode(point30)
-	fmt.Println(string(Logger.UnpackReceive("Received", buf[:n])))
+func handleConn(conn net.PacketConn) {
+	var buf [512]byte
 
-	os.Exit(0)
+	_, addr, err := conn.ReadFrom(buf[0:])
+	Logger.UnpackReceive("Received", buf[0:])
[…]

### 2015-05-01 src/instrumenter/instrumenter.go

@@ -52,7 +52,10 @@ func main() {
 	})
 
 	transformed = transformed + "\n" + extra_code
-	fmt.Println(transformed)
+
+	rp = regexp.MustCompile("[ ]*func[ ]+main\\(\\)[ ]+{")
+	//fmt.Println(transformed)
+	fmt.Println(rp.ReplaceAllString(transformed, "func main() {\n InstrumenterInit()\n"))
 	//fmt.Println(detectSendReceive(astFile))
 
 }
@@ -174,7 +177,7 @@ func GetAccessedVarsInScope(dumpNode *ast.Comment, f *ast.File, g *ast.File) []s
 
 	return results
 
-	//c := getWrapper(nil, "../TestPrograms/serverUDP.go")
+	//c := getWrapper(nil, "../TestPrograms/assignment1.go")
 
 	//for _, decl := range f.Decls {
 	//	//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
@@ -342,29 +345,35 @@ func GenerateDumpCode(vars []string, lineNumber int) string {
 var extra_code string = `
 
 var encoder *gob.Encoder
+
 func InstrumenterInit() {
-	fileW, _ := os.Create("log.txt")
+	fileW, _ := os.Create("log_client.txt")
 	encoder = gob.NewEncoder(fileW)
 }
 
 func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
 
 	length := len(varNames)
-	dumps := make([]NameValuePair, length)
+	dumps := make([]NameValuePair, 0)
 	for i := 0; i < length; i++ {
-		dumps[i].VarName = varNames[i]
-		dumps[i].Value = vars[i]
-		dumps[i].Type = reflect.TypeOf(vars[i]).String()
-	}
-	point := Point{dumps, lineNumber, Logger.GetCurrentVC()}
 
+		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
+			var dump NameValuePair
+			dump.VarName = varNames[i]
+			dump.Value = vars[i]
+			dump.Type = reflect.TypeOf(vars[i]).String()
+			dumps = append(dumps, dump)
+		}
+	}
+
+	point := Point{dumps, strconv.Itoa(lineNumber), Logger.GetCurrentVC()}
 	return point
 }
 
 type Point struct {
[…]

### 2015-05-01 Doc/approach.tex
changing dump to collect

@@
 
-Rather than dumping state at all program points we expect the
-developer to mark interesting program points using annotations. The
-program state will be dumped at only these annotated points. This will
+Rather than recording state at all program points we expect the
+developer to mark interesting program points using annotations. In our implementation developers need to put a comment \texttt{//@dump} after the program point. The
+program state will be collected at only these annotated points. This will
 also help to narrow down the focus to points that are identified by

### 2015-05-01 src/TestPrograms/serverudp_mod.go

@@ -1,106 +1,0 @@
-package main
-
-import (
-	"../govec"
-	"encoding/gob"
-	"fmt"
-	"net"
-	"os"
-	"reflect"
-	"strconv"
-	"time"
-)
-
-func main() {
-	InstrumenterInit()
-	Logger = govec.Initialize("Server", "testlog.log")
-	conn, err := net.ListenPacket("udp", ":8080")
-	//	if err != nil {
-	//		fmt.Println(err)
-	//		os.Exit(1)
-	//	}
-	printErr(err)
-
-	for {
-		if err != nil {
-			printErr(err)
-			continue
-		}
-		handleConn(conn)
-		fmt.Println("some one connected!")
-		vars27 := []interface{}{err, conn}
-		varsName27 := []string{"err", "conn"}
-		point27 := createPoint(vars27, varsName27, 27)
-		encoder.Encode(point27)
-	}
-	conn.Close()
-
-}
-
-func handleConn(conn net.PacketConn) {
-	var buf [512]byte
-
-	_, addr, err := conn.ReadFrom(buf[0:])
-	Logger.UnpackReceive("Received", buf[0:])
-	printErr(err)
-	msg := fmt.Sprintf("Hello There! time now is %s \n", time.Now().String())
-	conn.WriteTo(Logger.PrepareSend("Sending", []byte(msg)), addr)
-	vars41 := []interface{}{conn, buf, Logger, err, msg, addr}
-	varsName41 := []string{"conn", "buf", "Logger", "err", "msg", "addr"}
-	point41 := createPoint(vars41, varsName41, 41)
-	encoder.Encode(point41)
-}
-
-func printErr(err error) {
-	if err != nil {
-		fmt.Println(err)
-	}
-}
-
-var Logger *govec.GoLog
-
-var encoder *gob.Encoder
-
-func InstrumenterInit() {
-	fileW, _ := os.Create("log_server.txt")
-	encoder = gob.NewEncoder(fileW)
-}
-
-func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
-
-	length := len(varNames)
-	dumps := make([]NameValuePair, 0)
-	for i := 0; i < length; i++ {
-		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
-			var dump NameValuePair
[…]

### 2015-05-01 Doc/approach.tex
Some Changes

@@
 \begin{lstlisting}[caption={Sample code for Communication between 2 nodes - Node 0}, label=lst:node0]
-    Integer a := 1
-    Integer b := 2
+    a := 1
+    b := 2
     send ( a + '_' + b )
@@
     recv (buf)
-    Integer first := getFirstOperand( buf )
-    Integer second := getSecondOperand( buf )
-    Integer sum := first + second
+    first := getFirstOperand( buf )
+    second := getSecondOperand( buf )
+    sum := first + second
     send ( sum )
@@
 \end{minipage}\hfill
+\caption{An example program}
+\label{fig:exampleprog}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{go_flow.png}
+  \includegraphics[width=\columnwidth]{go_flow.pdf}
   \caption{Flow of the invariant inference of Go programs}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth,scale=0.5]{images/PDG-approach.png}
+\centering
+  \includegraphics[scale=0.3]{images/PDG-approach.png}
   \caption{Our approach to compute program dependence graph}
@@
 
-\subsection{Matching Logs with Vector Clocks}
+\subsection{Matching Logs with Vector Clocks and Feeding to Invariant Detector}
+
+Having the set of distributed state variables at each annotated point in the program by control and data flow analysis, we instrument the program so as to log these variables at the specified points.
+While logging variables, we also log the vector clock at the annotated point, this help us to match immediate logs across two nodes with each other and merge the logs and make a global snapshot of the system to form a consistent cut.
+We also log the type of each variable, so we can recover these variables from log file.
+Then, we convert each merged log to the specific format to be used as input for Daikon invariant detector and run the Daikon.
 

### 2015-05-01 Doc/evalrelate.tex
Some Changes

@@
-\subsection{Implementation}
+\section{Implementation Details}
 
-\subsubsection{Program Slicer}
+In this section we explain the details of prototype of our approach implemented in Go programming language.
+
+\subsection{Program Slicer}
 
@@
 
-\section{Results}
-We will implement our approach in a tool in Go programming language.
-We plan to evaluate our tool by verifying correctness of two-phase commit and leader election protocols.
-Our tool should be able to infer safety property of both algorithms.
-In two-phase commit protocol all nodes should perform the same action (commit or abort) so our tool should infer this property.
-In leader election algorithm there should be only one leader (uniqueness property) and at the end of protocol execution all nodes should know ID of the leader (agreement property).
-It is worth mentioning that our approach is not suitable for checking the liveness properties of these algorithms.
+\section{Evaluation}
+We implemented our approach in a tool in Go programming language.
+We evaluated our tool by verifying correctness of pseudo-two-phase commit of figure \ref{lst:2pc} and example program of figure \ref{fig:exampleprog}.
+Our tool was able to infer the expected invariants in both of these programs.
+Also, different components of our tool such as program slicer, instrumenter and log merger have been tested in isolation to ensure correctness of the prototype.
+It is worth mentioning, that our prototype currently only handles scalar variables but extending it to handle structs is only an extra engineering effort.
+%We also do not perform interprocedural data and control flow analysis, so we always log all global variables and
 
@@
 \section{Acknowledgment}
-We would like to thank Ivan Beschastnikh for his valuable insight and feedback on initial draft of this proposal.
+We would like to thank Ivan Beschastnikh for his valuable insight and feedback on proposal of this project.

### 2015-05-01 Doc/evalrelate.tex
More on Implementation

@@
-\section{Implementation Details}
+\subsection{Implementation Details}
 
@@
 
-\subsection{Program Slicer}
+\subsubsection{Program Instrumenter}
+
+We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree.
+Then we traverse this tree and collect informations about location of \texttt{//@dump} annotations and send and receive functions.
+Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.
+
+\subsubsection{Program Slicer}
 

### 2015-05-01 src/govec/govec.go

@@ -1,369 +1,0 @@
-package govec
-
-import "fmt"
-import "encoding/gob"
-import "bytes"
-import "./vclock"
-import "os"
-
-/*
-	- All licneces like other licenses ...
-
-	How to Use This Library
-
-	Step 1:
-	Create a Global Variable and Initialize it using like this =
-
-	Logger:= Initialize("MyProcess",ShouldYouSeeLoggingOnScreen,ShouldISendVectorClockonWire,Debug)
-
-	Step 2:
-	When Ever You Decide to Send any []byte , before sending call PrepareSend like this:
-	SENDSLICE := PrepareSend("Message Description", []YourPayload)
-	and send the SENDSLICE instead of your Designated Payload
-
-	Step 3:
-	When Receiveing, AFTER you receive your message, pass the []byte into UnpackRecieve
-	like this:
-
-	RETURNSLICE := UnpackReceive("Message Description" []ReceivedPayload)
-	and use RETURNSLICE for further processing.
-
-
-*/
-
-//This is the Global Variable Struct that holds all the info needed to be maintained
-type GoLog struct {
-
-	//Local Process ID
-	pid string
-
-	//Local vector clock in bytes
-	currentVC []byte
-
-	//Flag to Printf the logs made by Local Program
-	printonscreen bool
-
-	//This bools Checks to send the VC Bundled with User Data on the Wire
-	// if False, PrepareSend and UnpackReceive will simply forward their input
-	//buffer to output and locally log event. If True, VC will be encoded into packet on wire
-	VConWire bool
-
-	//activates/deactivates printouts at each preparesend and unpackreceive
-	debugmode bool
-
-	//Logfilename
-	logfile string
-}
-
-func (gv *GoLog) GetCurrentVC() []byte {
-	return gv.currentVC
-}
-
-//This is the data structure that is actually end on the wire
-type Data struct {
-	pid         []byte
-	vcinbytes   []byte
-	programdata []byte
-}
-
-//This function packs the Vector Clock with user program's data to send on wire
-func (d *Data) GobEncode() ([]byte, error) {
-	w := new(bytes.Buffer)
-	encoder := gob.NewEncoder(w)
-	err := encoder.Encode(d.pid)
-	if err != nil {
-		return nil, err
-	}
[…]

### 2015-05-01 Doc/evalrelate.tex
implementation

@@
 We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree.
-Then we traverse this tree and collect informations about location of \texttt{//@dump} annotations and send and receive functions.
+Then we traverse this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions.
 Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.
@@
 After building PDG, reachability of nodes from start node is determined via a breadth-first search on the graph.
+
+\subsubsection{Log Merger}
+
+We used go vector clocks \cite{vclock} to keep track of vector clocks and also our merge functionality is built on top of this implementation.
 

### 2015-05-01 Doc/introback.tex
some minor

@@
 In fact errors in distributed system should be defined on global state of the system and not on a single node.
-This also makes program comprehension of distributed systems a difficult task, since the developer needs to comprehend interaction of different nodes as well as logic of each node.
+This also makes program comprehension of distributed systems a difficult task, since the developer needs to comprehend interaction of different nodes as well as the logic of each node.
 
@@
 complex, providing invariants manually becomes more difficult.
-In this work, we automate the process of defining invariants for systems by inferring likely invariants of distributed systems from run time execution of systems.
-We define an invariant of distributed systems as a property that holds at a certain consistent cut across multiple nodes in distributed state of a distributed program.
+In this work, we automate the process of defining invariants by inferring likely invariants of distributed systems from run time execution.
+We define an invariant of distributed systems as a property that holds at a certain consistent cut across multiple nodes in distributed state of a distributed system.
 These inferred invariants can ease many programming tasks, such as program comprehension, bug prevention, debugging, verification and testing.
@@
 \centering
+\begin{minipage}{.45\textwidth}
 \begin{lstlisting}[caption={Coordinator Code}]
@@
 \end{lstlisting}
+\end{minipage}\hfill
+\begin{minipage}{.45\textwidth}
 \begin{lstlisting}[caption={Replica Code}]
@@
 \end{lstlisting}
+\end{minipage}\hfill
 \caption{Pseudo two phase commit code for coordinator and replicas}
@@
 
+%\begin{figure}
+%\centering
+%\begin{lstlisting}[caption={Coordinator Code}]
+%for i := 1 to n do
+%	send('Query',i)
+%commit := decide()
+%for i:= 1 to n do
+%	recv(buf,i)
+%	if (buf == 'Abort')
+%		commit := 'Abort'
+%for i := 1 to n
+%	send(commit, i)
+%\end{lstlisting}
+%\begin{lstlisting}[caption={Replica Code}]
+%recv(buf)
+%if(buf == 'Query')
+%	vote:= decide()
+%	send(vote)
+%if (vote == 'Abort')
+%	commit = 'Abort'
+%else
+%	recv(buf)
+%	commit = buf
+%\end{lstlisting}
+%\caption{Pseudo two phase commit code for coordinator and replicas}
+%\label{lst:2pc}
+%\end{figure}
+
 In this work we 
@@
 Not all variables of one node is affected by other nodes, we define the set of variables of one node whose values are affected by other nodes as distributed state variables of that node.
-We refer to set of distributed
+We refer to the set of distributed
 state variables of all nodes as distributed state of the system.
-We use Daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$), ordering ($y < x$) and containment ($x \in y$) relationships that may hold between the distributed state variables of all nodes in the system.
+We use Daikon \cite{ernst2001dynamically} to infer invariants between variables, so we can infer linear ($y = ax + b$) and ordering ($y < x$) relationships that may hold between the distributed state variables of all nodes in the system.
 

### 2015-05-01 src/programslicer/programslicer.go

@@ -1,5 +1,5 @@
 // ProgramSlicer
-package main
+package programslicer
 
 import (
 	"./cfg"
@@ -156,84 +156,84 @@ func ComputeBackwardSlice(start ast.Stmt, cfg *cfg.CFG, info *loader.PackageInfo
 	return slice
 }
 
-func main() {
-	src := `
-  package main
-  func foo(c int, nums []int) int {
-    //START
-    a := c      //6
-    var b int   //7
-    b += 1      //8
-    c, a = a, c //9
-    b = a       //10
-    for a, c = range nums { //11
-      b += a    //12
-    } // 13
-    a, c = c, a //14
-    c = b       //15
-    b++         //16
-    return a    //17
-    //END
-  }`
-	src = `
-	package main
+// func main() {
+// 	src := `
+//   package main
+//   func foo(c int, nums []int) int {
+//     //START
+//     a := c      //6
+//     var b int   //7
+//     b += 1      //8
+//     c, a = a, c //9
+//     b = a       //10
+//     for a, c = range nums { //11
+//       b += a    //12
+//     } // 13
+//     a, c = c, a //14
+//     c = b       //15
+//     b++         //16
+//     return a    //17
+//     //END
+//   }`
+// 	src = `
+// 	package main
 		
-func main() {
-	sum := 0
-	i := 1
-	for i < 11 {
-		sum = sum + i
-		i = i + 1
-	}
-	sum++
-	i++
-}
-`
+// func main() {
+// 	sum := 0
+// 	i := 1
+// 	for i < 11 {
+// 		sum = sum + i
+// 		i = i + 1
+// 	}
+// 	sum++
+// 	i++
+// }
+// `
 
-	var config loader.Config
-	f, err := config.ParseFile("testing", src)
-	if err != nil {
-		return // probably don't proceed
-	}
-	config.CreateFromFiles("testing", f)
-	prog, err := config.Load()
-	if err != nil {
-		return
-	}
+// 	var config loader.Config
+// 	f, err := config.ParseFile("testing", src)
+// 	if err != nil {
+// 		return // probably don't proceed
+// 	}
+// 	config.CreateFromFiles("testing", f)
+// 	prog, err := config.Load()
[…]

### 2015-05-01 Doc/evalrelate.tex
some minor
abstract and other minor fixes

@@
 We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree.
-Then we traverse this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions.
+Then we traversed this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions.
 Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.
@@
 It is worth mentioning, that our prototype currently only handles scalar variables but extending it to handle structs is only an extra engineering effort.
+The source code for our analysis and the experimental data are available online\cite{distproject} as open source software.
+
  %We also do not perform interprocedural data and control flow analysis, so we always log all global variables and

### 2015-05-01 Doc/introback.tex
abstract and other minor fixes

@@
 \section{Abstract}
+
+Inferred invariants can show specification of systems, act as documentation and help program comprehension.
+This is even more useful in a distributed system where the state is defined globally across nodes and errors are propogated across node boundaries.
+But defining invariants manually is a laborious task and not feasible for a typical software system.
+So we propose a technique for inferring likely invariants of distributed systems from run time execution.
+We use data flow and control flow analyses to identify what contributes to the distributed state of the system.
+Then we use executions of the program to get runtime values and then use Daikon to infer invariants between variables.
+To achieve this, we have implemented a program slicer for Go programs, an instrumentation framework and a program--trace analyzer in Go.
+For evaluating our tool, we have successfully inferred invariants in few distributed programs including the two-phase-commit algorithm.
+
 \section{Introduction}
@@
 We used vector clocks \cite{vectorclock} to partially order snapshots of the nodes in our system and form consistent cuts.
-The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes consists a significant portion of distributed state of that node.
-We use static data and control flow analysis to detect the distributed state of the system.
-To do so we computed the forward and backward slice of the program  \cite{programslice} from communication points in the program, such as receive and send functions, and determined list of variables whose values are affected by a receive function or can affect values that are sent by a send function.
+The notion of distributed state first proposed by Ousterhout in \cite{ousterhout1991role} as ``information retained in one place that describes something, or is determined by something, somewhere else in the system", we assume that variables whose value is affected by other nodes constitute a significant portion of distributed state of that node.
+We use static data flow and control flow analysis to identify the distributed state of the system.
+To do so we computed the forward and backward slices of the program  \cite{programslice} from communication points in the program, such as receive and send functions, and determined list of variables whose values are affected by a receive function or can affect values that are sent by a send function.
 By doing so, we identified the variables that contribute to interactions between nodes, possibly affect values of variables in other nodes, hence form the distributed state of the program.

### 2015-05-01 src/logmerger/LogMerger.go
moving log merger and adding line breaks

@@ -52,6 +52,7 @@ func createMapOfLogsForEachPoint(log []Point) map[string][]Point {
 
 func writeDeclaration(file *os.File, mapOfPoints map[string][]Point) {
 
+	file.WriteString("\n")
 	for _, v := range mapOfPoints {
 		point := v[0]
 		file.WriteString(fmt.Sprintf("ppt p-%s:::%s\n", point.LineNumber, point.LineNumber))
@@ -65,6 +66,7 @@ func writeDeclaration(file *os.File, mapOfPoints map[string][]Point) {
 			file.WriteString(fmt.Sprintf("comparability -1\n"))
 
 		}
+		file.WriteString("\n")
 
 	}
 }

### 2015-05-01 src/govec/vclock/vclock.go
Fixing Log Merger

@@ -33,11 +33,11 @@
 package vclock
 
 import (
-	"bytes"
 	"errors"
-	"fmt"
 	"math"
 	"sort"
+	"fmt"
+	"bytes"
 	"strconv"
 )
 
@@ -85,34 +85,33 @@ func (vc *VClock) FindTicks(id string) (curt uint64, found bool) {
 
 func (vc *VClock) PrintVC() {
 	fmt.Print("{")
-	for i := range vc.items {
+	for i:= range vc.items {
 		fmt.Print("\"")
 		fmt.Print(vc.items[i].id)
 		fmt.Print("\":")
 		fmt.Print(vc.items[i].ticks)
-		if i+1 < len(vc.items) {
+		if(i+1 < len(vc.items)){
 			fmt.Print(", ")
 		}
 	}
 	fmt.Println("}")
 }
 
-func (vc *VClock) ReturnVCString() string {
+func (vc *VClock) ReturnVCString() (string) {
 	var buffer bytes.Buffer
 	buffer.WriteString("{")
-	for i := range vc.items {
+	for i:= range vc.items {
 		buffer.WriteString("\"")
 		buffer.WriteString(vc.items[i].id)
 		buffer.WriteString("\":")
-		buffer.WriteString(strconv.FormatUint(vc.items[i].ticks, 10))
-		if i+1 < len(vc.items) {
+		buffer.WriteString(strconv.FormatUint(vc.items[i].ticks,10))
+		if(i+1 < len(vc.items)){
 			buffer.WriteString(", ")
 		}
 	}
 	buffer.WriteString("}")
 	return buffer.String()
 }
-
 // updateItem changes or appends the given id with ticks and when.
 func (vc *VClock) updateItem(id string, ticks, when uint64) {
 	if when > 0 {
@@ -168,48 +167,6 @@ func (vc *VClock) LastUpdate() (last uint64) {
 		}
 	}
 	return last
-}
-
-func (vc *VClock) Matches(other *VClock) bool {
-	lenVC := (float64)(len(vc.items))
-	lenOther := (float64)(len(other.items))
-
-	difference := math.Abs(lenVC - lenOther)
-
-	if difference > 1 {
-		return false
-	}
-	numDiff := 0
-	for oi := 0; oi != len(other.items); oi++ {
-		if vci, found := vc.findItem(other.items[oi].id); found {
-			otherTicks := (float64)(other.items[oi].ticks)
[…]

### 2015-05-01 src/instrumenter/assignment1_mod.go

@@ -1,0 +1,100 @@
+package main
+
+import (
+	"../govec"
+	"encoding/gob"
+	"fmt"
+	"net"
+	"os"
+	"reflect"
+	"strconv"
+)
+
+func main() {
+ InstrumenterInit()
+
+	Logger = govec.Initialize("Client", "testclient.log")
+
+	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
+	printErr(errR)
+	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
+	printErr(errL)
+
+	conn, errDial := net.DialUDP("udp", lAddr, rAddr)
+	printErr(errDial)
+
+	// sending UDP packet to specified address and port
+	msg := "get me the message !"
+	_, errWrite := conn.Write(Logger.PrepareSend("Asking time", []byte(msg)))
+	printErr(errWrite)
+
+	// Reading the response message
+	var buf [1024]byte
+	n, errRead := conn.Read(buf[0:])
+	printErr(errRead)
+	incoming_msg := string(Logger.UnpackReceive("Received", buf[:n]))
+	fmt.Println(">>>" + incoming_msg)
+	vars32 := []interface{}{Logger,msg,buf,errRead,n,lAddr,errDial,conn,errWrite,incoming_msg,errR,errL,rAddr}
+varsName32 := []string{"Logger","msg","buf","errRead","n","lAddr","errDial","conn","errWrite","incoming_msg","errR","errL","rAddr"}
+point32 := createPoint(vars32, varsName32, 32)
+encoder.Encode(point32)
+
+	os.Exit(0)
+}
+
+func printErr(err error) {
+	if err != nil {
+		fmt.Println(err)
+		os.Exit(1)
+	}
+}
+
+var Logger *govec.GoLog
+
+
+
+var encoder *gob.Encoder
+
+func InstrumenterInit() {
+	fileW, _ := os.Create("../TestPrograms/assignment1.go.txt")
+	encoder = gob.NewEncoder(fileW)
+}
+
+func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
+
+	length := len(varNames)
+	dumps := make([]NameValuePair, 0)
+	for i := 0; i < length; i++ {
+
+		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
[…]

### 2015-05-01 src/instrumenter/instrumenter.go

@@ -26,6 +26,7 @@ const (
 	END   = 100000000
 )
 
+var src_location string = "../TestPrograms/assignment1.go"
 var fset *token.FileSet
 var astFile *ast.File
 var c *CFGWrapper
@@ -61,7 +62,8 @@ func main() {
 }
 
 func initializeInstrumenter() string {
-	src_location := "../TestPrograms/assignment1.go"
+	
+	extra_code = fmt.Sprintf(extra_code, src_location)
 	// Create the AST by parsing src.
 	fset = token.NewFileSet() // positions are relative to fset
 	astFile, _ = parser.ParseFile(fset, src_location, nil, parser.ParseComments)
@@ -341,13 +343,12 @@ func GenerateDumpCode(vars []string, lineNumber int) string {
 
 	return buffer.String()
 }
-
 var extra_code string = `
 
 var encoder *gob.Encoder
 
 func InstrumenterInit() {
-	fileW, _ := os.Create("log_client.txt")
+	fileW, _ := os.Create("%s.txt")
 	encoder = gob.NewEncoder(fileW)
 }
 
@@ -382,13 +383,14 @@ type NameValuePair struct {
 	Type    string
 }
 
-func (nvp NameValuePair) String() string {
-	return fmt.Sprintf("(%s,%s,%s)", nvp.VarName, nvp.Value, nvp.Type)
-}
+// func (nvp NameValuePair) String() string {
+// 	return fmt.Sprintf("(%s,%s,%s)", nvp.VarName, nvp.Value, nvp.Type)
+// }
 
-func (p Point) String() string {
-	return fmt.Sprintf("%s : %s", p.LineNumber, p.Dump)
-}`
+// func (p Point) String() string {
+// 	return fmt.Sprintf("%s : %s", p.LineNumber, p.Dump)
+// }
+`
 
 func addImports() {
 	packagesToImport := []string{"\"encoding/gob\"", "\"os\"", "\"reflect\"", "\"strconv\""}

### 2015-05-01 src/logmerger/LogMerger.go

@@ -6,12 +6,13 @@ import (
 	"encoding/gob"
 	"fmt"
 	"os"
+	"strings"
 	//"reflect"
 )
 
 func main() {
-	log1 := readLog("TestPrograms/log_client.txt")
-	log2 := readLog("TestPrograms/log_server.txt")
+	log1 := readLog("../TestPrograms/assignment1.go.txt")
+	log2 := readLog("../TestPrograms/serverUDP.go.txt")
 	addNodeName("client.", log1)
 	addNodeName("server.", log2)
 	fmt.Println(log1[0])
@@ -52,6 +53,8 @@ func createMapOfLogsForEachPoint(log []Point) map[string][]Point {
 
 func writeDeclaration(file *os.File, mapOfPoints map[string][]Point) {
 
+	file.WriteString("decl-version 2.0\n")
+	file.WriteString("var-comparability none\n")
 	file.WriteString("\n")
 	for _, v := range mapOfPoints {
 		point := v[0]
@@ -83,12 +86,14 @@ func writeValues(file *os.File, log []Point) {
 			if variable.Type == "int" {
 				file.WriteString(fmt.Sprintf("%d\n", variable.Value))
 			} else {
-				file.WriteString(fmt.Sprintf("%s\n", variable.Value))
-			}
+				file.WriteString(strings.Replace(fmt.Sprintf("%s", variable.Value),"\n"," ",-1)+"\n")
+			} 
+
 
 			file.WriteString(fmt.Sprintf("1\n"))
 
 		}
+		file.WriteString("\n")
 
 	}
 }

### 2015-05-01 src/instrumenter/instrumenter.go
GetAffectedVars

@@ -10,6 +10,7 @@ import (
 	"golang.org/x/tools/go/ast/astutil"
 	//"os"
 	//"reflect"
+	"../programslicer"
 	"regexp"
 	"strings"
 	"testing"
@@ -17,8 +18,8 @@ import (
 	"golang.org/x/tools/go/loader"
 	"golang.org/x/tools/go/types"
 
-	"github.com/godoctor/godoctor/analysis/cfg"
-	"github.com/godoctor/godoctor/analysis/dataflow"
+	"../programslicer/cfg"
+	"../programslicer/dataflow"
 )
 
 const (
@@ -26,23 +27,41 @@ const (
 	END   = 100000000
 )
 
-var src_location string = "../TestPrograms/assignment1.go"
+var src_location string = "../TestPrograms/serverUDP.go"
 var fset *token.FileSet
 var astFile *ast.File
 var c *CFGWrapper
 
 func main() {
+
+	optimize := false
+
 	source := initializeInstrumenter()
 	dumpNodes := GetDumpNodes()
 
 	var generated_code []string
-	for _, dump := range dumpNodes {
-		//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
-		//fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
-		line := c.fset.Position(dump.Pos()).Line
-		//fmt.Println(line)
-		generated_code = append(generated_code, GenerateDumpCode(GetAccessedVarsInScope(dump, astFile, c.f), line))
 
+	if !optimize {
+		for _, dump := range dumpNodes {
+			//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+			//fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
+			line := c.fset.Position(dump.Pos()).Line
+			//fmt.Println(line)
+			// log all vars
+			generated_code = append(generated_code, GenerateDumpCode(GetAccessedVarsInScope(dump, astFile, c.f), line))
+
+		}
+
+	} else {
+		for _, dump := range dumpNodes {
+			//fmt.Println(GetAccessibleVarsInScope(int(dumps.Slash), astFile))
+			//fmt.Println(GetAccessedVarsInScope(dump, astFile, c.f))
+			line := c.fset.Position(dump.Pos()).Line
+			//fmt.Println(line)
+			// log all vars
[…]

### 2015-05-01 src/instrumenter/assignment1_mod.go
Removing modified assignment1

@@ -1,100 +1,0 @@
-package main
-
-import (
-	"../govec"
-	"encoding/gob"
-	"fmt"
-	"net"
-	"os"
-	"reflect"
-	"strconv"
-)
-
-func main() {
- InstrumenterInit()
-
-	Logger = govec.Initialize("Client", "testclient.log")
-
-	rAddr, errR := net.ResolveUDPAddr("udp4", ":8080")
-	printErr(errR)
-	lAddr, errL := net.ResolveUDPAddr("udp4", ":18585")
-	printErr(errL)
-
-	conn, errDial := net.DialUDP("udp", lAddr, rAddr)
-	printErr(errDial)
-
-	// sending UDP packet to specified address and port
-	msg := "get me the message !"
-	_, errWrite := conn.Write(Logger.PrepareSend("Asking time", []byte(msg)))
-	printErr(errWrite)
-
-	// Reading the response message
-	var buf [1024]byte
-	n, errRead := conn.Read(buf[0:])
-	printErr(errRead)
-	incoming_msg := string(Logger.UnpackReceive("Received", buf[:n]))
-	fmt.Println(">>>" + incoming_msg)
-	vars32 := []interface{}{Logger,msg,buf,errRead,n,lAddr,errDial,conn,errWrite,incoming_msg,errR,errL,rAddr}
-varsName32 := []string{"Logger","msg","buf","errRead","n","lAddr","errDial","conn","errWrite","incoming_msg","errR","errL","rAddr"}
-point32 := createPoint(vars32, varsName32, 32)
-encoder.Encode(point32)
-
-	os.Exit(0)
-}
-
-func printErr(err error) {
-	if err != nil {
-		fmt.Println(err)
-		os.Exit(1)
-	}
-}
-
-var Logger *govec.GoLog
-
-
-
-var encoder *gob.Encoder
-
-func InstrumenterInit() {
-	fileW, _ := os.Create("../TestPrograms/assignment1.go.txt")
-	encoder = gob.NewEncoder(fileW)
-}
-
-func createPoint(vars []interface{}, varNames []string, lineNumber int) Point {
-
-	length := len(varNames)
-	dumps := make([]NameValuePair, 0)
-	for i := 0; i < length; i++ {
-
-		if vars[i] != nil && ((reflect.TypeOf(vars[i]).Kind() == reflect.String) || (reflect.TypeOf(vars[i]).Kind() == reflect.Int)) {
[…]

### 2015-05-01 src/instrumenter/instrumenter.go
Some changes to instrumenter

@@ -93,6 +93,7 @@ func getAffectedVars() []string {
 
 	for _, node := range sendNodes {
 		recvStmt := (*node).(ast.Stmt)
+
 		vars := programslicer.GetBackwardAffectedVariables(recvStmt, c.cfg, c.prog.Created[0], c.prog.Fset)
 		affectedVars = append(affectedVars, vars...)
 	}
@@ -139,16 +140,20 @@ func initializeInstrumenter() string {
 func detectReceive(f *ast.File) []*ast.Node {
 	var results []*ast.Node
 	ast.Inspect(f, func(n ast.Node) bool {
-		switch x := n.(type) {
-		case *ast.CallExpr:
-			switch y := x.Fun.(type) {
-			case *ast.SelectorExpr:
-				left, ok := y.X.(*ast.Ident)
-				if ok && left.Name == "conn" && y.Sel.Name == "ReadFrom" {
-					//fmt.Println(left.Name, y.Sel.Name)
-					results = append(results, &n)
+		switch z := n.(type) {
+		case *ast.ExprStmt:
+			switch x := z.X.(type) {
+			case *ast.CallExpr:
+				switch y := x.Fun.(type) {
+				case *ast.SelectorExpr:
+					left, ok := y.X.(*ast.Ident)
+					if ok && left.Name == "conn" && y.Sel.Name == "ReadFrom" {
+						//fmt.Println(left.Name, y.Sel.Name)
+						results = append(results, &n)
+					}
 				}
 			}
+
 			return true
 		}
 
@@ -160,14 +165,17 @@ func detectReceive(f *ast.File) []*ast.Node {
 func detectSend(f *ast.File) []*ast.Node {
 	var results []*ast.Node
 	ast.Inspect(f, func(n ast.Node) bool {
-		switch x := n.(type) {
-		case *ast.CallExpr:
-			switch y := x.Fun.(type) {
-			case *ast.SelectorExpr:
-				left, ok := y.X.(*ast.Ident)
-				if ok && left.Name == "conn" && y.Sel.Name == "WriteTo" {
-					//fmt.Println(left.Name, y.Sel.Name)
-					results = append(results, &n)
+		switch z := n.(type) {
+		case *ast.ExprStmt:
+			switch x := z.X.(type) {
+			case *ast.CallExpr:
+				switch y := x.Fun.(type) {
+				case *ast.SelectorExpr:
+					left, ok := y.X.(*ast.Ident)
[…]

### 2015-05-01 Doc/evalrelate.tex
Change format of abstract
minor edits

@@
 We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree.
-Then we traversed this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions.
+Then we traversed this tree and collected informations about locations of \texttt{//@dump} annotations and send and receive functions.
 Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.
@@
 
+In this phase we use \texttt{encoding/gob} package to decode data items corresponding to each program point written to the log.
 We used go vector clocks \cite{vclock} to keep track of vector clocks and also our merge functionality is built on top of this implementation.

### 2015-05-01 src/vclock/vclock.go
vclock mod

@@ -208,7 +208,7 @@ func (vc *VClock) Matches(other *VClock) bool {
 		}
 	}
 
-	return numDiff == 1
+	return numDiff == 1 || numDiff == 2 || numDiff == 3
 
 }
 

### 2015-05-01 Doc/approach.tex

@@
 statements which will write the values of variable to a file when the
-program reaches that point in the runtime. Since there can be multiple points annotated in a program by a
+program reaches that point in the runtime.
+The annotation detection is shown in Block 1 of the flow diagram in Figure~\ref{fig:go_flow}.
+Re-writing the source is done at the Block 3 of the flow diagram in Figure~\ref{fig:go_flow}.
+Since there can be multiple points annotated in a program by a
 developer, vector clocks will be used to partially order annotation
@@
 To compute these distributed state variables, we developed a Go program slicer which we explain in the following section.
+This dataflow analysis phase is shown in Block 2 of the flow diagram in Figure~\ref{fig:go_flow}.
 
@@
 Then, we convert each merged log to the specific format to be used as input for Daikon invariant detector and run the Daikon.
+This log merging is done at the Block 5 of the flow diagram in Figure~\ref{fig:go_flow}.
 
